### 2016-04-18 papers/asonam2016/paper.tex
Add paper source files

\documentclass[conference]{IEEEtran}
\usepackage[style=ieee, backend=biber]{biblatex}

\ifCLASSINFOpdf
	\usepackage[pdftex]{graphicx}
	\graphicspath{{img/}}
	\DeclareGraphicsExtensions{.pdf,.jpg,.png}
\else
	\usepackage[dvips]{graphicx}
 	\graphicspath{{img/}}
	\DeclareGraphicsExtensions{.pdf,.jpg,.png}
\fi

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\bibliography{paper.bib}

\begin{document}
\title{Mimicry in Online Conversations: An Exploratory Study of Linguistic Analysis Techniques}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Tom Carrick, Awais Rashid, Paul J Taylor}
\IEEEauthorblockA{Security Lancaster / CREST\\
Lancaster University\\
Lancaster, United Kingdom\\
Email: \{t.carrick, a.rashid, p.j.taylor\} @lancaster.ac.uk}
\and
\IEEEauthorblockN{Adam Joinson}
\IEEEauthorblockA{???\\
University of Bath\\
Bath, United Kingdom\\
Email: a.joinson@bath.ac.uk}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The Interactive Alignment Model is the prevailing theory of
[I probably need some help phrasing this].
In this study we investigate how several linguistic alignment techniques can be used
to detect mimicry at the lexical, syntactic and situational levels of the
Interactive Alignment Model.

We show that [something].
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart

Mimicry in online conversations is an important area of research [something about insider threats
and maybe something about improving outcomes of tasks, using mimicry in AI, etc.]

There are a number of measures designed to capture mimicry in text, [something something], and some
efforts have been made to compare and trial these techniques. However, few of these techniques are 
grounded what cognitive science knows about how mimicry works within humans.

[Maybe should mention here that LILLA and SILLA do mention lexical/syntactic levels explicitly which
is probably the exception. Everything else either naturally fits into a layer (HAM), haven't really
been used for mimicry before as far as I know (word/paragraph vectors), or aren't specifically
targeted at a layer (LSM, Zelig). Not sure if I want to mention all this in the introduction though.]

This perspective is important so that each measure is grounded [too much grounded] in reality.
Moreover, it suggests [does it?] that the best approach may be to combine existing measures to create
a more holistic measure. [don't like any of this wording].

[I feel like I want a "this study aims to x y and z" here]

\section{Background}

[if we only want to discuss IAM here should we retitle this section?]

The Interactive Alignment Model (IAM)\cite{pickering2004toward} is an attempt to model alignment in
conversations. It consists of six layers, which with the exception of the top layer, the situation model,
are all representations of some aspect of speech.

\begin{enumerate}
	\item The situation model --- a representation of the situation being discussed
	\item The semantic representation --- the meaning of the utterance
	\item The syntactic representation --- the sentence structure
	\item The lexical representation --- the choice of words used
	\item The phonological representation --- [I have no idea how to describe the difference between
		phonology and phonetics]
	\item The phonetic representation --- something
\end{enumerate}

[Do we really need both list and figure?]

The phonological and phonetic layers are ignored by this paper as they do not relate to written text.
[should I just leave them out of the list?]

The theory states that alignment "percolates" between layers such that increased alignment in one layer
will lead to increased alignment in other layers.

\begin{figure*}
	\caption{The interactive alignment model}
	\includegraphics[width=\textwidth]{iam}
\end{figure*}

[Figure takes up over half a page. Might be an idea to use a different one, or cut off phon* layers.
Not sure if I can go around stealing people's images either.]

\section{Method}
I'm not exactly sure what experiments we will have yet,
or if we need to name this section something else entirely.

Do we maybe have a subsection for each layer and a subsubsection for each measure?
We should explain somewhere why we skip situation, phonological and phonetic layers.

\subsection{Lexical}
Lexical stuff.

\subsubsection{LILLA}
LILLA\cite{wang2014linguistic, xu2015evaluation}

\subsubsection{HAM}
HAM\cite{doyle2016robust}

\subsection{Syntactic}
Syntactic stuff.

\subsubsection{SILLA}
SILLA

\subsubsection{SHAM}
SHAM

\subsection{Semantic}
Semantic

\subsubsection{word2vec}
word2vec\cite{mikolov2013distributed}

\subsubsection{doc2vec}
doc2vec\cite{le2014distributed}. Consider also sense2vec\cite{trask2015sense2vec} and/or doc2vec sense2vec hybrid?

\subsection{Other Measures}
Other

\subsubsection{Linguistic Style Matching}
LSM\cite{niederhoffer2002linguistic}

\subsubsection{Zelig}
Zelig\cite{jones2014finding}

\section{Results}
Same here, not sure what results we will have.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion and Future Work}
The conclusion goes here.

\section{Discussion}
Discussion

% use section* for acknowledgment
\section*{Acknowledgment}
Do we need to thank CREST for giving us money here?

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

\printbibliography

\end{document}

### 2016-04-18 twtr/get_tweets.py
Add twitter data extraction stuff.

@@ -1,0 +1,86 @@
+import os
+import pickle
+import sys
+
+import tweepy
+
+
+CONSUMER_KEY = os.environ['TWITTER_CONSUMER_KEY']
+CONSUMER_SECRET = os.environ['TWITTER_CONSUMER_SECRET']
+ACCESS_TOKEN = os.environ['TWITTER_ACCESS_TOKEN']
+ACCESS_TOKEN_SECRET = os.environ['ACCESS_TOKEN_SECRET']
+
+
+auth = tweepy.OAuthHandler(CONSUMER_KEY, CONSUMER_SECRET)
+auth.set_access_token(ACCESS_TOKEN, ACCESS_TOKEN_SECRET)
+
+api = tweepy.API(auth, wait_on_rate_limit=True, wait_on_rate_limit_notify=True)
+
+
+def get_status_chain(api, status_id):
+    """Given a status ID, iterate up the chain of tweets and return them in order.
+
+    This function doesn't look further down the chain, it only looks up, so it could be incomplete.
+    We also stop short if we hit a third author, as we only care about dyads.
+
+    Keyword arguments:
+    api -- tweepy API object
+    status_id -- ID of the status to start from
+    """
+    authors = []
+    statuses = []
+
+    while True:
+        status = api.get_status(status_id)
+        author = status.author.screen_name
+
+        # Check we're in a dyadic conversation.
+        if len(authors) < 2 and author not in authors:
+            authors.append(author)
+        elif author not in authors:
+            # No longer a dyad, cut off at this status and only use the dyadic part.
+            break
+
+        statuses.append(status)
+
+        if not status.in_reply_to_status_id_str:
+            break
+
+        status_id = status.in_reply_to_status_id_str
+
+    statuses.reverse()
+    return statuses
+
+
+chains = []
+
+page = 1
+while len(chains) < 200:
+    statuses = None
+    while statuses is None:
+        try:
+            statuses = api.search(q='filter:replies', count=100, lang='en')
+        except Exception as e:
+            print('Error: {error}. Retrying.'.format(error=e), file=sys.stderr)
+
+    if statuses:
+        for status in statuses:
+            try:
+                status_chain = get_status_chain(api, status.id_str)
+                if len(status_chain) > 9:
+                    chains.append(status_chain)
+            except Exception as e:
+                # We hit a private message or a connection issue, skip to the next.
+                print('Error: {error}. Continuing.'.format(error=e), file=sys.stderr)
[…]

### 2016-04-18 twtr/load_test.py

@@ -1,0 +1,12 @@
+import pickle
+
+
+with open('tweets.pickle', 'rb') as f:
+    chains = pickle.load(f)
+
+print(len(chains))
+
+for chain in chains:
+    print(len(chain))
+    for tweet in chain:
+        print(tweet.text)

### 2016-04-18 twtr/select_tweets.py

@@ -1,0 +1,28 @@
+import pickle
+
+from distutils.util import strtobool
+
+
+def query_yes_no(question, default="yes"):
+    print('{question} [y/n]'.format(question=question))
+    while True:
+        try:
+            return strtobool(input().lower())
+        except ValueError:
+            print("Please respond with 'y' or 'n'.")
+
+
+with open('tweets.pickle', 'rb') as f:
+    chains = pickle.load(f)
+
+keepers = []
+for chain in chains:
+    for status in chain:
+        print('{author}: {status}'.format(author=status.author.screen_name, status=status.text))
+    is_keeper = query_yes_no('Do you want to keep this chain?')
+
+    if is_keeper:
+        keepers.append(chain)
+
+with open('selected_tweets.pickle', 'wb') as f:
+    pickle.dump(keepers, f)

### 2016-04-18 twtr/tweets_to_text.py

@@ -1,0 +1,13 @@
+import pickle
+
+
+with open('selected_tweets.pickle', 'rb') as f:
+    chains = pickle.load(f)
+
+
+with open('data.txt', 'w') as f:
+    for counter, chain in enumerate(chains):
+        f.write('Chain {num}\n'.format(num=counter + 1))
+        for status in chain:
+            f.write('{author}: {status}\n'.format(author=status.author.screen_name, status=status.text))
+        f.write('------------------------------------------------\n\n')

### 2016-04-19 measures/deps.py
Add measures, start tweet parsing

@@ -1,0 +1,7 @@
+def subtrees(doc):
+    deps = []
+    for word in doc:
+        children = list(word.children)
+        if len(children):
+            deps.append((word.dep, [child.dep for child in children]))
+    return deps

### 2016-04-19 measures/lla.py

@@ -1,0 +1,17 @@
+from . import deps
+
+
+def lla(target, prime):
+    counter = 0
+    for token in target:
+        counter += prime.count(token)
+
+    return counter / (len(prime) * len(target))
+
+
+def lilla(target, prime):
+    return lla(target, prime)
+
+
+def silla(target, prime):
+    return lla(deps.subtrees(target), deps.subtrees(prime))

### 2016-04-19 measures/lsm.py

@@ -1,0 +1,27 @@
+import statistics
+
+
+FUNCTION_CLASSES = {'ADP', 'AUX', 'CONJ', 'DET', 'INTJ', 'NUM', 'PART', 'PRON', 'SCONJ'}
+
+
+def lsm(doc):
+    doc_length = len(doc)
+    function_words = {function_class: 0 for function_class in FUNCTION_CLASSES}
+    for token in doc:
+        if token.pos_ in FUNCTION_CLASSES:
+            function_words[token.pos_] += 1
+
+    return {word_class: (count / doc_length) * 100 for word_class, count in function_words.items()}
+
+
+def dyad_lsm(doc1, doc2):
+    lsm1 = lsm(doc1)
+    lsm2 = lsm(doc2)
+    scores = []
+    for word_class in FUNCTION_CLASSES:
+        try:
+            scores.append(1 - abs(lsm1[word_class] - lsm2[word_class]) / (lsm1[word_class] + lsm2[word_class]))
+        except ZeroDivisionError:
+            scores.append(1)
+
+    return statistics.mean(scores)

### 2016-04-19 measures/util.py

@@ -1,0 +1,3 @@
+def remove_whitespace(doc):
+    """Return a list of non-whitespace tokens in doc."""
+    return [token for token in doc if token.string.strip()]

### 2016-04-19 run_measures.py

@@ -1,0 +1,4 @@
+from spacy.en import English
+from textblob import TextBlob
+
+from measures import lla, lsm

### 2016-04-19 twtr/load_test.py

@@ -1,12 +1,0 @@
-import pickle
-
-
-with open('tweets.pickle', 'rb') as f:
-    chains = pickle.load(f)
-
-print(len(chains))
-
-for chain in chains:
-    print(len(chain))
-    for tweet in chain:
-        print(tweet.text)

### 2016-04-19 twtr/parse_tweets.py

@@ -1,0 +1,18 @@
+import os
+import pickle
+
+
+def get_authors(chain):
+    a = chain[0].author.screen_name
+    b = next(status.author.screen_name for status in chain[1:] if status.author.screen_name != a)
+    return a, b
+
+
+DIR = os.path.dirname(os.path.realpath(__file__))
+DATA_DIR = os.path.join(DIR, 'data')
+
+with open(os.path.join(DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+for chain in chains:
+    print(get_authors(chain))

### 2016-04-19 twtr/parse_tweets.py
Make get_authors() less ugly.

@@ -2,14 +2,13 @@ import os
 import pickle
 
 
-def get_authors(chain):
-    a = chain[0].author.screen_name
-    b = next(status.author.screen_name for status in chain[1:] if status.author.screen_name != a)
-    return a, b
-
-
 DIR = os.path.dirname(os.path.realpath(__file__))
 DATA_DIR = os.path.join(DIR, 'data')
+
+
+def get_authors(chain):
+    return set(status.author.screen_name for status in chain)
+
 
 with open(os.path.join(DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)

### 2016-04-20 generate_html.py
Add HTML generator

@@ -1,0 +1,50 @@
+import itertools
+import os
+import pickle
+
+from twtr import utils
+
+
+BASE_DIR = os.path.dirname(os.path.realpath(__file__))
+DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
+HTML_DIR = os.path.join(BASE_DIR, 'html')
+
+
+with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+parsed_chains = utils.parse_chains(chains)
+
+html = """
+<meta charset="utf-8">
+<title>Test</title>
+<script src="https://twemoji.maxcdn.com/twemoji.min.js"></script>
+<style>
+  /*
+    EmojiSymbols Font (c)blockworks - Kenichi Kaneko
+    http://emojisymbols.com/
+  */
+  @font-face {
+    font-family: "EmojiSymbols";
+    src: url('EmojiSymbols-Regular.woff') format('woff');
+    text-decoration: none;
+    font-style: normal;
+  }
+  body {
+    font-family: 'EmojiSymbols', sans-serif;
+    line-height: 1;
+    font-size: 24px;
+  }
+</style>
+"""
+
+for counter, chain in parsed_chains.items():
+    html += '<h1>Conversation {counter}</h1>'.format(counter=counter + 1)
+    author = itertools.cycle('AB')
+    for message in chain:
+        html += '<p><strong>{author}</strong>: {message}</p>'.format(
+            author=next(author), message=message
+        ).replace('\n', '<br>')
+
+with open(os.path.join(HTML_DIR, 'messages.html'), 'w') as f:
+    f.write(html)

### 2016-04-20 run_measures.py

@@ -1,4 +1,14 @@
-from spacy.en import English
-from textblob import TextBlob
+import os
+import pickle
 
-from measures import lla, lsm
+from twtr import utils
+
+
+BASE_DIR = os.path.dirname(os.path.realpath(__file__))
+DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
+
+
+with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+parsed_chains = utils.parse_chains(chains)

### 2016-04-20 twtr/parse_tweets.py

@@ -1,17 +1,0 @@
-import os
-import pickle
-
-
-DIR = os.path.dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(DIR, 'data')
-
-
-def get_authors(chain):
-    return set(status.author.screen_name for status in chain)
-
-
-with open(os.path.join(DIR, 'selected_tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-for chain in chains:
-    print(get_authors(chain))

### 2016-04-20 twtr/utils.py

@@ -1,0 +1,45 @@
+import html
+import itertools
+import validators
+
+
+def normalise_urls(text):
+    for word in text.split(' '):
+        if validators.url(word):
+            text = text.replace(word, '[URL]')
+    return text
+
+
+def remove_screen_names(text):
+    while True:
+        text = text.lstrip()
+        word = text.split(' ')[0]
+        if not word.startswith('@'):
+            break
+
+        text = text.replace(word, '')
+    return text
+
+
+def format_message(text, escape_html=True):
+    text = remove_screen_names(text)
+    text = normalise_urls(text)
+    if escape_html:
+        text = html.unescape(text)
+    return text.strip()
+
+
+def parse_chains(chains, escape_html=True):
+    parsed_chains = {}
+    for counter, chain in enumerate(chains):
+        messages = []
+        for key, group in itertools.groupby(chain, lambda x: x.author.screen_name):
+            merged = []
+            for status in group:
+                merged.append(format_message(status.text))
+
+            merged = '\n'.join(merged)
+            messages.append(merged)
+
+        parsed_chains[counter] = messages
+    return parsed_chains

### 2016-04-20 run_measures.py
Don't escape entities during HTML generation

@@ -11,4 +11,4 @@ DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
 with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
-parsed_chains = utils.parse_chains(chains)
+parsed_chains = utils.parse_chains(chains, escape_html=False)

### 2016-04-20 twtr/utils.py

@@ -36,7 +36,7 @@ def parse_chains(chains, escape_html=True):
         for key, group in itertools.groupby(chain, lambda x: x.author.screen_name):
             merged = []
             for status in group:
-                merged.append(format_message(status.text))
+                merged.append(format_message(status.text, escape_html))
 
             merged = '\n'.join(merged)
             messages.append(merged)

### 2016-04-20 generate_html.py
Better font for emoji

@@ -17,21 +17,16 @@ parsed_chains = utils.parse_chains(chains)
 
 html = """
 <meta charset="utf-8">
-<title>Test</title>
-<script src="https://twemoji.maxcdn.com/twemoji.min.js"></script>
+<title>Messages to classify</title>
 <style>
-  /*
-    EmojiSymbols Font (c)blockworks - Kenichi Kaneko
-    http://emojisymbols.com/
-  */
   @font-face {
-    font-family: "EmojiSymbols";
-    src: url('EmojiSymbols-Regular.woff') format('woff');
+    font-family: 'Symbola';
+    src: url('Symbola.ttf') format('truetype');
     text-decoration: none;
     font-style: normal;
   }
   body {
-    font-family: 'EmojiSymbols', sans-serif;
+    font-family: 'Symbola', sans-serif;
     line-height: 1;
     font-size: 24px;
   }

### 2016-04-23 papers/asonam2016/paper.tex
Progress

@@
 
-[Maybe should mention here that LILLA and SILLA do mention lexical/syntactic levels explicitly which
-is probably the exception. Everything else either naturally fits into a layer (HAM), haven't really
-been used for mimicry before as far as I know (word/paragraph vectors), or aren't specifically
-targeted at a layer (LSM, Zelig). Not sure if I want to mention all this in the introduction though.]
-
-This perspective is important so that each measure is grounded [too much grounded] in reality.
+This perspective is important so that each measure is grounded in reality.
 Moreover, it suggests [does it?] that the best approach may be to combine existing measures to create
@@
 
-[I feel like I want a "this study aims to x y and z" here]
+Of the measures discussed in this paper, only one has attempted to measure alignment with this in mind
+and some, such as LSM seem to work outside of the theory altogether.
 
-\section{Background}
+This paper aims to compare how well existing linguistic analysis techniques work to detect mimicry in 
+relation to the Interactive Alignment Model. Further, we also look at some existing techniques that 
+have not previously been used to detect mimicry and discuss their viability.
 
-[if we only want to discuss IAM here should we retitle this section?]
+[Not sure what else to put here. Section II does this, section III looks at that type thing?]
 
+\section{Related Work}
+This paper draws from many sources for its measures. The most similar piece of work is a comparison
+of several methods\cite{xu2015evaluation}, some discussed in this paper. It does not, however, try
+to compare the accuracy of the measures, rather, it [does some stuff I don't understand that well,
+seems like it looks at some statistical properties?]
+
+[Not sure what else to mention here]
+
+\section{The Interactive Alignment Model}
 The Interactive Alignment Model (IAM)\cite{pickering2004toward} is an attempt to model alignment in
-conversations. It consists of six layers, which with the exception of the top layer, the situation model,
-are all representations of some aspect of speech.
+conversations. It consists of six layers, which with the exception of the top layer, the situation
+model, are all representations of some aspect of speech.
 
@@
 
-[Do we really need both list and figure?]
-
 The phonological and phonetic layers are ignored by this paper as they do not relate to written text.
-[should I just leave them out of the list?]
 
@@
 
-[Figure takes up over half a page. Might be an idea to use a different one, or cut off phon* layers.
-Not sure if I can go around stealing people's images either.]
+\section{Method}
 
-\section{Method}
-I'm not exactly sure what experiments we will have yet,
-or if we need to name this section something else entirely.
+\subsection{Data}
+The dataset consists of 103 dyadic conversations taken from Twitter. Tweets were found via Twitter's 
+search API, using English language and being a reply as criteria. We then work up the chain of tweets 
+until we hit the end, or a third interlocutor is found, at which point the conversation is cut off and 
+kept, as long as there are no fewer than 10 tweets in the conversation. 200 tweets were found using 
+this method. Of these, 62 were removed as they were not true conversations (either monologues or 
+collaborative fiction writing/roleplay). 18 conversations were removed as they had significant amounts 
+of non-English text, and 17 conversations involved bots and were also removed.
 
-Do we maybe have a subsection for each layer and a subsubsection for each measure?
-We should explain somewhere why we skip situation, phonological and phonetic layers.
+The data is processed as follows:
+\begin{itemize}
+	\item Screen names at the start of the message are removed. These are just the names of the 
+		  interlocutors and only add noise.
+	\item All URLs are replace with the string '[URL]'.
+	\item HTML entities such as \&amp; are converted to plain text (\&).
+	\item Any adjacent messages by the same author are merged together such that each message always
+	      alternates between the two interlocutors.
+\end{itemize}
+
+The data was classified by three PhD students at Lancaster University with backgrounds in mimicry. Each 
+conversation was classified for lexical, syntactic and semantic mimicry on a three point scale where 0 
+represents no mimicry, 1 represents low levels of mimicry at that layer, and 2 represents high levels 
+of mimicry.
+
+Each measure, with exceptions noted in following subsections [Probably just HAM at this point],
+is then run against the data such that each message from author A is compared with each message from 
+author B that occurred before the original message.
+\footnote{[I could probably make my github repo public and put a link to the code here?]}
+
+[Need to justify dataset and discuss limitations]
 
@@
 \subsubsection{LILLA}
-LILLA\cite{wang2014linguistic, xu2015evaluation}
+Lexical Indiscriminate Local Linguistic Alignment (LILLA)\cite{wang2014linguistic, xu2015evaluation}
+is a measure that explicitly works at the lexical layer. It gives the probability that a word from the 
+prime document will appear at a particular position in the target document. It is defined as:
+
+\[LILLA(target, prime) = \frac{p(target|prime)}{p(target)}\]
 
 \subsubsection{HAM}
-HAM\cite{doyle2016robust}
+The Hierarchical Alignment Model (HAM)\cite{doyle2016robust} ...
 
@@
 \subsubsection{SILLA}
-SILLA
+Syntactic Indiscriminate Local Linguistic Alignment (SILLA)
 
@@
 \subsubsection{doc2vec}
-doc2vec\cite{le2014distributed}. Consider also sense2vec\cite{trask2015sense2vec} and/or doc2vec sense2vec hybrid?
+doc2vec\cite{le2014distributed}.
 
@@
 \section{Results}
-Same here, not sure what results we will have.
+Still not sure how to compare everything.
 
@@
 \section*{Acknowledgment}
-Do we need to thank CREST for giving us money here?
+The authors gratefully acknowledge a grant from CREST (probably need to find the name of this).
 

### 2016-04-23 measures/lla.py

@@ -6,7 +6,10 @@ def lla(target, prime):
     for token in target:
         counter += prime.count(token)
 
-    return counter / (len(prime) * len(target))
+    try:
+        return counter / (len(prime) * len(target))
+    except ZeroDivisionError:
+        return 1.0
 
 
 def lilla(target, prime):

### 2016-04-23 measures/util.py

@@ -1,3 +1,0 @@
-def remove_whitespace(doc):
-    """Return a list of non-whitespace tokens in doc."""
-    return [token for token in doc if token.string.strip()]

### 2016-04-23 run_measures.py

@@ -1,14 +1,38 @@
 import os
 import pickle
 
+from spacy.en import English
+from textblob import TextBlob
+
+from measures import lla, lsm
 from twtr import utils
 
 
 BASE_DIR = os.path.dirname(os.path.realpath(__file__))
 DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
 
+nlp = English()
+
 
 with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 parsed_chains = utils.parse_chains(chains, escape_html=False)
+
+for chain_id, chain in parsed_chains.items():
+    messages_a = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[::2]]
+    messages_b = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[1::2]]
+
+    for counter, message_a in enumerate(messages_a, 1):
+        for message_b in messages_b[counter:]:
+            lilla_score = lla.lilla(message_a['textblob'].words, message_b['textblob'].words)
+            silla_score = lla.silla(message_a['spacy'], message_b['spacy'])
+            lsm_score = lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])
+            wv_score = message_a['spacy'].similarity(message_b['spacy'])
+
+    for counter, message_b in enumerate(messages_b, 1):
+        for message_a in messages_a[counter:]:
+            lilla_score = lla.lilla(message_a['textblob'].words, message_b['textblob'].words)
+            silla_score = lla.silla(message_a['spacy'], message_b['spacy'])
+            lsm_score = lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])
+            wv_score = message_a['spacy'].similarity(message_b['spacy'])

### 2016-04-23 twtr/select_tweets.py

@@ -1,6 +1,10 @@
+import os
 import pickle
 
 from distutils.util import strtobool
+
+
+DATA_DIR = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'data')
 
 
 def query_yes_no(question, default="yes"):
@@ -12,7 +16,7 @@ def query_yes_no(question, default="yes"):
             print("Please respond with 'y' or 'n'.")
 
 
-with open('tweets.pickle', 'rb') as f:
+with open(os.path.join(DATA_DIR, 'tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 keepers = []
@@ -24,5 +28,5 @@ for chain in chains:
     if is_keeper:
         keepers.append(chain)
 
-with open('selected_tweets.pickle', 'wb') as f:
+with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'wb') as f:
     pickle.dump(keepers, f)

### 2016-04-23 twtr/tweets_to_text.py

@@ -6,8 +6,8 @@ with open('selected_tweets.pickle', 'rb') as f:
 
 
 with open('data.txt', 'w') as f:
-    for counter, chain in enumerate(chains):
-        f.write('Chain {num}\n'.format(num=counter + 1))
+    for counter, chain in enumerate(chains, 1):
+        f.write('Chain {num}\n'.format(num=counter))
         for status in chain:
             f.write('{author}: {status}\n'.format(author=status.author.screen_name, status=status.text))
         f.write('------------------------------------------------\n\n')

### 2016-04-25 papers/asonam2016/paper.tex
More progress

@@
 In this study we investigate how several linguistic alignment techniques can be used
-to detect mimicry at the lexical, syntactic and situational levels of the
+to detect mimicry at the lexical, syntactic and situation levels of the
 Interactive Alignment Model.
@@
 
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
@@
 \section{Introduction}
-% no \IEEEPARstart
 
-Mimicry in online conversations is an important area of research [something about insider threats
-and maybe something about improving outcomes of tasks, using mimicry in AI, etc.]
+Mimicry in online conversations is an important and active area of research. Humans tend to mimic each
+other in many areas, such as speech
+\cite{levelt1982surface, bock1986syntactic, bock1989closed, garrod1987saying},
+physical actions\cite{bernieri1988coordinated}
+and written text{\cite{danescu2011chameleons, scissors2008linguistic}.
+People that mimic each other's language have more successful outcomes in joint tasks
+\cite{maddux2008chameleons}. Additionally, mimicry can be an indicator of insider threats
+\cite{taylor2013detecting}.
 
-There are a number of measures designed to capture mimicry in text, [something something], and some
-efforts have been made to compare and trial these techniques. However, few of these techniques are 
-grounded what cognitive science knows about how mimicry works within humans.
+There are a number of measures designed to capture mimicry in text, and some efforts have been made to
+compare and trial these techniques. However, few of these techniques are grounded what cognitive 
+science knows about how mimicry works within humans.
 
 This perspective is important so that each measure is grounded in reality.
-Moreover, it suggests [does it?] that the best approach may be to combine existing measures to create
-a more holistic measure. [don't like any of this wording].
+Moreover, it suggests that the best approach may be to combine existing measures to create
+a more holistic technique for mimicry detection.
 
-Of the measures discussed in this paper, only one has attempted to measure alignment with this in mind
-and some, such as LSM seem to work outside of the theory altogether.
+The most similar piece of work is a comparison of several methods\cite{xu2015evaluation}, some 
+discussed in this paper. However, it does not try to directly compare the accuracy of the measures,
+nor does it look at how they fit into the Interactive Alignment Model.
 
@@
 
-[Not sure what else to put here. Section II does this, section III looks at that type thing?]
+The novel contributions of this paper are:
+\begin{itemize}
+	\item Compares existing mimicry detection techniques and how they map to the
+		  Interactive Alignment Model
+	\item Trials techniques that have not been used for mimicry detection before.
+	\item Looks at creating hybrid techniques, combining measures together to find if they are more 
+		  accurate when combined. 
+\end{itemize}
 
-\section{Related Work}
-This paper draws from many sources for its measures. The most similar piece of work is a comparison
-of several methods\cite{xu2015evaluation}, some discussed in this paper. It does not, however, try
-to compare the accuracy of the measures, rather, it [does some stuff I don't understand that well,
-seems like it looks at some statistical properties?]
-
-[Not sure what else to mention here]
+This paper is divided into six sections. The next section introduces the
+Interactive Alignment Model, the psychological model of mimicry we are testing our techniques against.
+Section III gives a background of each measure tested in the paper, and defines which layer of the
+IAM (if any) the measure falls into.
+Section IV addresses the data collected and how it is processed for each technique.
+We follow in section V with a discussion of the results, and finally give our conclusions and
+suggestions for further work in section VI.
 
@@
 	\item The lexical representation --- the choice of words used
-	\item The phonological representation --- [I have no idea how to describe the difference between
-		phonology and phonetics]
-	\item The phonetic representation --- something
+	\item The phonological representation --- ???
+	\item The phonetic representation --- the sounds of an utterance
 \end{enumerate}
 
-The phonological and phonetic layers are ignored by this paper as they do not relate to written text.
+The phonological and phonetic representations are not discussed in this paper as they relate purely
+to the sound of speech, representations that do not exist in the written text of online conversations.
 
-The theory states that alignment "percolates" between layers such that increased alignment in one layer
-will lead to increased alignment in other layers.
+Further, the situation model is not included as there are currently no measures that can be used for
+finding alignment at the situational level.
+
+The theory states that alignment is automatic, that conversation partners will align their speech 
+towards each other at every level of the model. In addition, alignment "percolates" between layers such
+that increased alignment in one layer will lead to increased alignment in other layers.
 
@@
 
+\section{Analysis Techniques}
+
+\subsection{Local Linguistic Alignment}
+Local Linguistic Alignment (LLA) is a simple,  dual purpose method that can work at both the lexical
+and syntactic layers\cite{wang2014linguistic, xu2015evaluation}.
+
+Lexical Indiscriminate Local Linguistic Alignment (LILLA) works at the lexical layer. It gives the
+probability that a word from the prime document will appear at a particular position in the target 
+document. It is defined as:
+
+\[LILLA(target, prime) = \frac{p(target|prime)}{p(target)}\]
+
+Syntactic Indiscriminate Local Linguistic Alignemnt (SILLA) works at the syntactic layer. It works
+in exactly the same way as LILLA, but rather than compare words, each sentence is annotated with a
+phrase structure tree, and LLA is run on these instead. As such, it measures the probability of a
+phrase structure subtree in the prime document appearing occurring at a given position in the target
+document.
+
+\subsection{Hierarchical Alignment Model}
+\cite{doyle2016robust}
+
+\subsection{Word Vectors}
+word2vec\cite{mikolov2013distributed}
+doc2vec\cite{le2014distributed}.
+
+\subsection{Linguistic Style Matching}
+\cite{niederhoffer2002linguistic}
+
 \section{Method}
-
-\subsection{Data}
 The dataset consists of 103 dyadic conversations taken from Twitter. Tweets were found via Twitter's 
@@
 
-The data was classified by three PhD students at Lancaster University with backgrounds in mimicry. Each 
-conversation was classified for lexical, syntactic and semantic mimicry on a three point scale where 0 
-represents no mimicry, 1 represents low levels of mimicry at that layer, and 2 represents high levels 
-of mimicry.
+[LIMITATIONS]
 
-Each measure, with exceptions noted in following subsections [Probably just HAM at this point],
-is then run against the data such that each message from author A is compared with each message from 
-author B that occurred before the original message.
+The data was classified by three researchers with backgrounds in mimicry independent of the authors of 
+this paper.
+Each  conversation was classified for lexical, syntactic and semantic mimicry on a three point scale 
+where 0 represents no mimicry, 1 represents low levels of mimicry at that layer, and 2 represents high 
+levels of mimicry. Classifications from each author were averaged together to give each conversation
+three scores between 0 and 2.
+
+Each measure is then run against the data such that each message from author A is compared with each 
+message from author B that occurred before the original message. The exception for this is HAM,
+where we have used the original implementation [need to actually do this and explain it further].
 \footnote{[I could probably make my github repo public and put a link to the code here?]}
-
-[Need to justify dataset and discuss limitations]
-
-\subsection{Lexical}
-Lexical stuff.
-
-\subsubsection{LILLA}
-Lexical Indiscriminate Local Linguistic Alignment (LILLA)\cite{wang2014linguistic, xu2015evaluation}
-is a measure that explicitly works at the lexical layer. It gives the probability that a word from the 
-prime document will appear at a particular position in the target document. It is defined as:
-
-\[LILLA(target, prime) = \frac{p(target|prime)}{p(target)}\]
-
-\subsubsection{HAM}
-The Hierarchical Alignment Model (HAM)\cite{doyle2016robust} ...
-
-\subsection{Syntactic}
-Syntactic stuff.
-
-\subsubsection{SILLA}
-Syntactic Indiscriminate Local Linguistic Alignment (SILLA)
-
-\subsubsection{SHAM}
-SHAM
-
-\subsection{Semantic}
-Semantic
-
-\subsubsection{word2vec}
-word2vec\cite{mikolov2013distributed}
-
-\subsubsection{doc2vec}
-doc2vec\cite{le2014distributed}.
-
-\subsection{Other Measures}
-Other
-
-\subsubsection{Linguistic Style Matching}
-LSM\cite{niederhoffer2002linguistic}
-
-\subsubsection{Zelig}
-Zelig\cite{jones2014finding}
 
@@
 
+\section{Discussion}
+Discussion
+
 \section{Conclusion and Future Work}
 The conclusion goes here.
-
-\section{Discussion}
-Discussion
+Zelig\cite{jones2014finding}
 

### 2016-04-25 export_to_ham.py

@@ -1,0 +1,64 @@
+import csv
+import os
+import pickle
+
+from twtr import utils
+
+
+BASE_DIR = os.path.dirname(os.path.realpath(__file__))
+DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
+
+
+with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+
+def build_user_tsv():
+    fieldnames = ['uid', 'screenname', 'verified', 'numtweets', 'numfriends', 'numfollowers', 'numlistsin',
+                  'numfavoritesgiven', 'creationyear', 'creationmonth', 'creationdate']
+    for conversation_id, chain in enumerate(chains, 1):
+        authors = {status.author for status in chain}
+        with open(os.path.join(DATA_DIR, 'ham', conversation_id.zfill(3) + '_users.tsv')) as f:
+            writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
+            for author in authors:
+                writer.writerow({
+                    'uid': author.id_str,
+                    'screenname': author.screen_name,
+                    'verified': author.verified,
+                    'numtweets': author.statuses_count,
+                    'numfriends': author.friends_count,
+                    'numfollowers': author.followers_count,
+                    'numlistsin': author.listed_count,
+                    'numfavoritesgiven': author.favourites_count,
+                    'creationyear': author.created_at.year,
+                    'creationmonth': author.created_at.month,
+                    'creationdate': author.created_at.day,
+                })
+
+
+def build_status_tsv():
+    fieldnames = ['msguser', 'msgtext', 'replyid', 'replyuser', 'replytext']
+
+    for conversation_id, chain in enumerate(chains, 1):
+        with open(os.path.join(DATA_DIR, 'ham', conversation_id.zfill(3) + '.tsv')) as f:
+            writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
+            previous_status = None
+            for status in chain:
+                if conversation_id == 1:
+                    previous_status = status
+                    continue
+
+                assert status.in_reply_to_status_id_str == previous_status.id_str
+
+                writer.writerow({
+                    'msgid': status.id_str,
+                    'msguser': status.author.id_str,
+                    'msgtext': utils.format_message(status.text, is_ham=True),
+                    'replyid': previous_status.id_str,
[…]

### 2016-04-25 generate_csv.py

@@ -1,0 +1,12 @@
+import csv
+import os
+
+
+HTML_DIR = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'html')
+
+
+with open(os.path.join(HTML_DIR, 'classifications.csv'), 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(['', 'Lexical', 'Syntactic', 'Semantic'])
+    for row in range(103):
+        writer.writerow(['Conversation {counter}'.format(counter=row + 1), '', '', ''])

### 2016-04-25 generate_data_csv.py

@@ -1,0 +1,28 @@
+import csv
+import itertools
+import os
+import pickle
+
+from twtr import utils
+
+
+BASE_DIR = os.path.dirname(os.path.realpath(__file__))
+DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
+
+
+with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+parsed_chains = utils.parse_chains(chains)
+
+with open(os.path.join(DATA_DIR, 'data.csv'), 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(['Text'])
+    for chain in parsed_chains.values():
+        row = ''
+        author = itertools.cycle('AB')
+        for message in chain:
+            row += '<p><strong>{author}</strong>: {message}</p>'.format(
+                author=next(author), message=message
+            ).replace('\n', '<br>')
+        writer.writerow([row])

### 2016-04-25 twtr/utils.py

@@ -10,6 +10,13 @@ def normalise_urls(text):
     return text
 
 
+def normalise_screen_names(text):
+    for word in text.split(' '):
+        if word.startswith('@'):
+            text = text.replace(word, '[MENTION]')
+    return text
+
+
 def remove_screen_names(text):
     while True:
         text = text.lstrip()
@@ -21,8 +28,11 @@ def remove_screen_names(text):
     return text
 
 
-def format_message(text, escape_html=True):
-    text = remove_screen_names(text)
+def format_message(text, escape_html=True, is_ham=False):
+    if is_ham:
+        text = normalise_screen_names(text)
+    else:
+        text = remove_screen_names(text)
     text = normalise_urls(text)
     if escape_html:
         text = html.unescape(text)

### 2016-04-25 export_to_ham.py
Fix HAM export

@@ -18,7 +18,7 @@ def build_user_tsv():
                   'numfavoritesgiven', 'creationyear', 'creationmonth', 'creationdate']
     for conversation_id, chain in enumerate(chains, 1):
         authors = {status.author for status in chain}
-        with open(os.path.join(DATA_DIR, 'ham', conversation_id.zfill(3) + '_users.tsv')) as f:
+        with open(os.path.join(DATA_DIR, 'ham', str(conversation_id).zfill(3) + '_users.tsv'), 'w') as f:
             writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
             for author in authors:
                 writer.writerow({
@@ -37,14 +37,14 @@ def build_user_tsv():
 
 
 def build_status_tsv():
-    fieldnames = ['msguser', 'msgtext', 'replyid', 'replyuser', 'replytext']
+    fieldnames = ['msgid', 'msguser', 'msgtext', 'replyid', 'replyuser', 'replytext']
 
     for conversation_id, chain in enumerate(chains, 1):
-        with open(os.path.join(DATA_DIR, 'ham', conversation_id.zfill(3) + '.tsv')) as f:
+        with open(os.path.join(DATA_DIR, 'ham', str(conversation_id).zfill(3) + '.tsv'), 'w') as f:
             writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
             previous_status = None
-            for status in chain:
-                if conversation_id == 1:
+            for counter, status in enumerate(chain):
+                if counter == 0:
                     previous_status = status
                     continue
 
@@ -56,8 +56,9 @@ def build_status_tsv():
                     'msgtext': utils.format_message(status.text, is_ham=True),
                     'replyid': previous_status.id_str,
                     'replyuser': previous_status.author.id_str,
-                    'replytext': previous_status.replytext.id_str,
+                    'replytext': utils.format_message(previous_status.text, is_ham=True),
                 })
+                previous_status = status
 
 
 build_user_tsv()

### 2016-04-27 measures/lsm.py
Small LSM tweak

@@ -19,9 +19,6 @@ def dyad_lsm(doc1, doc2):
     lsm2 = lsm(doc2)
     scores = []
     for word_class in FUNCTION_CLASSES:
-        try:
-            scores.append(1 - abs(lsm1[word_class] - lsm2[word_class]) / (lsm1[word_class] + lsm2[word_class]))
-        except ZeroDivisionError:
-            scores.append(1)
+        scores.append(1 - abs(lsm1[word_class] - lsm2[word_class]) / (lsm1[word_class] + lsm2[word_class] + .0001))
 
     return statistics.mean(scores)

### 2016-04-27 papers/asonam2016/paper.tex
ASONAM paper progress

@@
 Lancaster, United Kingdom\\
-Email: \{t.carrick, a.rashid, p.j.taylor\} @lancaster.ac.uk}
-\and
-\IEEEauthorblockN{Adam Joinson}
-\IEEEauthorblockA{???\\
-University of Bath\\
-Bath, United Kingdom\\
-Email: a.joinson@bath.ac.uk}}
+Email: \{t.carrick, a.rashid, p.j.taylor\} @lancaster.ac.uk}}
 
@@
 In this study we investigate how several linguistic alignment techniques can be used
-to detect mimicry at the lexical, syntactic and situation levels of the
+to detect mimicry at the lexical, syntactic and semantic levels of the
 Interactive Alignment Model.
@@
 
-Mimicry in online conversations is an important and active area of research. Humans tend to mimic each
-other in many areas, such as speech
-\cite{levelt1982surface, bock1986syntactic, bock1989closed, garrod1987saying},
-physical actions\cite{bernieri1988coordinated}
-and written text{\cite{danescu2011chameleons, scissors2008linguistic}.
-People that mimic each other's language have more successful outcomes in joint tasks
-\cite{maddux2008chameleons}. Additionally, mimicry can be an indicator of insider threats
-\cite{taylor2013detecting}.
+Mimicry in online conversations is an important and active area of research.
+Humans tend to mimic each other in many areas, such as speech \cite{levelt1982surface, bock1986syntactic, bock1989closed, garrod1987saying}, physical actions \cite{bernieri1988coordinated} and written text \cite{danescu2011chameleons, scissors2008linguistic}.
 
-There are a number of measures designed to capture mimicry in text, and some efforts have been made to
-compare and trial these techniques. However, few of these techniques are grounded what cognitive 
-science knows about how mimicry works within humans.
+Existing research has shown that people who mimic each other’s language have more successful outcomes in joint tasks \cite{maddux2008chameleons}.
+Hence, detection of mimicry can be a valuable indicator in understanding group dynamics in collaborative settings.
+It can also play a role in other application areas, e.g., for detection of insider threats \cite{taylor2013detecting}.
 
-This perspective is important so that each measure is grounded in reality.
-Moreover, it suggests that the best approach may be to combine existing measures to create
-a more holistic technique for mimicry detection.
+There are a number of measures designed to capture mimicry in text, and some efforts have been made to compare and trial these techniques.
+However, few of these techniques are grounded in what cognitive  science knows about how mimicry works within humans.
 
-The most similar piece of work is a comparison of several methods\cite{xu2015evaluation}, some 
-discussed in this paper. However, it does not try to directly compare the accuracy of the measures,
-nor does it look at how they fit into the Interactive Alignment Model.
-
-This paper aims to compare how well existing linguistic analysis techniques work to detect mimicry in 
-relation to the Interactive Alignment Model. Further, we also look at some existing techniques that 
-have not previously been used to detect mimicry and discuss their viability.
-
-The novel contributions of this paper are:
+This paper addresses this limitation by contrasting how well existing linguistic analysis techniques work to detect mimicry in relation to the Interactive Alignment Model.
+Further, we also consider some existing techniques that have not previously been used to detect mimicry and discuss their viability.
+The novel contributions of this paper are as follows:
 \begin{itemize}
-	\item Compares existing mimicry detection techniques and how they map to the
-		  Interactive Alignment Model
-	\item Trials techniques that have not been used for mimicry detection before.
-	\item Looks at creating hybrid techniques, combining measures together to find if they are more 
-		  accurate when combined. 
+	\item We compare existing mimicry detection techniques and how they map to the Interactive Alignment Model 
+	\item  We evaluate techniques that have not been used for mimicry detection before and discuss their feasibility in this regard.
+	\item On the basis of our analysis, we posit that hybrid techniques, composing multiple measures, may offer a more holistic approach for mimicry detection.
 \end{itemize}
 
-This paper is divided into six sections. The next section introduces the
-Interactive Alignment Model, the psychological model of mimicry we are testing our techniques against.
-Section III gives a background of each measure tested in the paper, and defines which layer of the
-IAM (if any) the measure falls into.
-Section IV addresses the data collected and how it is processed for each technique.
-We follow in section V with a discussion of the results, and finally give our conclusions and
-suggestions for further work in section VI.
+Existing work has compared several methods, e.g., \cite{xu2015evaluation}, including some discussed in this paper.
+However, such works do not aim to contrast the effectiveness of the measures with regards to cognitive models such as the Interactive Alignment Model.
+To our knowledge, our work is the first to undertake such a comparison.
+
+The rest of this paper is structured as follows.
+In Section II, we briefly introduce the Interactive Alignment Model - the psychological model of mimicry against which we test our techniques.
+Section III provides a brief introduction to each measure tested in the paper, and defines the layer of the IAM (if any) in which the measure resides.
+Section IV describes the data set used in our analysis.
+Section V presents the results of our analysis and highlights the importance of composing multiple measures.
+Finally, Section VI concludes the paper and identifies directions for future work.
 
 \section{The Interactive Alignment Model}
-The Interactive Alignment Model (IAM)\cite{pickering2004toward} is an attempt to model alignment in
+The Interactive Alignment Model (IAM) \cite{pickering2004toward} is an attempt to model alignment in
 conversations. It consists of six layers, which with the exception of the top layer, the situation
@@
 Local Linguistic Alignment (LLA) is a simple,  dual purpose method that can work at both the lexical
-and syntactic layers\cite{wang2014linguistic, xu2015evaluation}.
+and syntactic layers \cite{wang2014linguistic, xu2015evaluation}.
 
@@
 Syntactic Indiscriminate Local Linguistic Alignemnt (SILLA) works at the syntactic layer. It works
-in exactly the same way as LILLA, but rather than compare words, each sentence is annotated with a
+in exactly the same way as LILLA, but instead of comparing words, each sentence is annotated with a
 phrase structure tree, and LLA is run on these instead. As such, it measures the probability of a
@@
 \subsection{Hierarchical Alignment Model}
-\cite{doyle2016robust}
+The Hierarchical Alignment Model (HAM) \cite{doyle2016robust} is ...
+So it finds the most common words, uses these as markers, then looks at how often these markers
+appear.
 
-\subsection{Word Vectors}
-word2vec\cite{mikolov2013distributed}
-doc2vec\cite{le2014distributed}.
+\subsection{Word and Document Vectors}
+Word2vec \cite{mikolov2013efficient, mikolov2013distributed} is a machine learning technique that,
+given a word, tries to predict the two adjacent words. Each word is then mapped to vector space
+and can be directly compared. The closer the two word vectors to each other, the more semantically
+related they are.
 
-\subsection{Linguistic Style Matching}
-\cite{niederhoffer2002linguistic}
+Doc2vec \cite{le2014distributed} works on the same principle as Word2vec. Here, each word is mapped to
+a unique vector, and each paragraph is also mapped to a vector, which contribute to predicting the next
+word in the paragraph. It can be used with not only paragraphs, but with sentences or entire documents.
+
+[I can't find any pretrained doc2vec models trained on twitter data and don't have the data to do it
+myself so this might end up relegated to future work]
+
+\subsection{Language Style Matching}
+Language Style Matching (LSM) \cite{ireland2010language, ireland2011language}
+is a measure that counts the usage of function words by an interlocutor.
+For each class of function word (e.g., determiners, pronouns, adpositions), the number of words is 
+calculated as a percentage of the total document, which is the score for each class. Scores are 
+calculated between the dyad using a weighted difference, shown below, and these scores averaged to 
+produce a single LSM score for that dyad.
+
+\[ LSM_{class} = 1 - [(|class_1 - class_2|)] / (class_1 + class_2 + .0001) \]
 
@@
 collaborative fiction writing/roleplay). 18 conversations were removed as they had significant amounts 
-of non-English text, and 17 conversations involved bots and were also removed.
+of non-English text. 17 conversations involved bots and were also removed.
 
-The data is processed as follows:
+The data was processed as follows:
 \begin{itemize}
-	\item Screen names at the start of the message are removed. These are just the names of the 
+	\item Screen names at the start of the message were removed. These are just the names of the 
 		  interlocutors and only add noise.
-	\item All URLs are replace with the string '[URL]'.
-	\item HTML entities such as \&amp; are converted to plain text (\&).
-	\item Any adjacent messages by the same author are merged together such that each message always
+	\item All URLs were replaced with the string '[URL]'.
+	\item HTML entities such as \&amp; were converted to plain text (\&).
+	\item Any adjacent messages by the same author were merged together such that each message always
 	      alternates between the two interlocutors.
@@
 
-[LIMITATIONS]
+The dataset is small, which is both an advantage as it is possible to classify the data manually
+and a disadvantage in that the sample size is smaller. We did not actively seek out mimicry by
+targeting our search as it was important to have conversations that would test negatively for mimicry
+as well as positively.
 
@@
 
-Each measure is then run against the data such that each message from author A is compared with each 
-message from author B that occurred before the original message. The exception for this is HAM,
-where we have used the original implementation [need to actually do this and explain it further].
+Each measure was then run against the data such that each message from author A is compared with each 
+message from author B that occurred before the original message.
+
+HAM is treated differently as it requires data to be set up in a different way.
+Here we have reused the original implementation, and have formatted the data into tab separated
+values files with each row being a pair of tweets, with an extra TSV file to store user information.
 \footnote{[I could probably make my github repo public and put a link to the code here?]}
@@
 The conclusion goes here.
-Zelig\cite{jones2014finding}
+Zelig \cite{jones2014finding}
 
@@
 \section*{Acknowledgment}
-The authors gratefully acknowledge a grant from CREST (probably need to find the name of this).
+This research is funded by the Engineering and Social Sciences (ESRC) Centre for Behavioural and Social Science Approaches to Security (CREST).
 

### 2016-04-28 core/constants.py
Refactor constants

@@ -1,0 +1,6 @@
+import os
+
+
+BASE_DIR = BASE_DIR = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))
+DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
+HTML_DIR = os.path.join(BASE_DIR, 'html')

### 2016-04-28 export_to_ham.py

@@ -2,14 +2,11 @@ import csv
 import os
 import pickle
 
+from core import constants
 from twtr import utils
 
 
-BASE_DIR = os.path.dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
-
-
-with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 
@@ -18,7 +15,7 @@ def build_user_tsv():
                   'numfavoritesgiven', 'creationyear', 'creationmonth', 'creationdate']
     for conversation_id, chain in enumerate(chains, 1):
         authors = {status.author for status in chain}
-        with open(os.path.join(DATA_DIR, 'ham', str(conversation_id).zfill(3) + '_users.tsv'), 'w') as f:
+        with open(os.path.join(constants.DATA_DIR, 'ham', str(conversation_id).zfill(3) + '_users.tsv'), 'w') as f:
             writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
             for author in authors:
                 writer.writerow({
@@ -40,7 +37,7 @@ def build_status_tsv():
     fieldnames = ['msgid', 'msguser', 'msgtext', 'replyid', 'replyuser', 'replytext']
 
     for conversation_id, chain in enumerate(chains, 1):
-        with open(os.path.join(DATA_DIR, 'ham', str(conversation_id).zfill(3) + '.tsv'), 'w') as f:
+        with open(os.path.join(constants.DATA_DIR, 'ham', str(conversation_id).zfill(3) + '.tsv'), 'w') as f:
             writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
             previous_status = None
             for counter, status in enumerate(chain):

### 2016-04-28 generate_csv.py

@@ -1,11 +1,10 @@
 import csv
 import os
 
+from core import constants
 
-HTML_DIR = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'html')
 
-
-with open(os.path.join(HTML_DIR, 'classifications.csv'), 'w') as csvfile:
+with open(os.path.join(constants.HTML_DIR, 'classifications.csv'), 'w') as csvfile:
     writer = csv.writer(csvfile)
     writer.writerow(['', 'Lexical', 'Syntactic', 'Semantic'])
     for row in range(103):

### 2016-04-28 generate_data_csv.py

@@ -3,19 +3,16 @@ import itertools
 import os
 import pickle
 
+from core import constants
 from twtr import utils
 
 
-BASE_DIR = os.path.dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
-
-
-with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 parsed_chains = utils.parse_chains(chains)
 
-with open(os.path.join(DATA_DIR, 'data.csv'), 'w') as csvfile:
+with open(os.path.join(constants.DATA_DIR, 'data.csv'), 'w') as csvfile:
     writer = csv.writer(csvfile)
     writer.writerow(['Text'])
     for chain in parsed_chains.values():

### 2016-04-28 generate_html.py

@@ -2,15 +2,11 @@ import itertools
 import os
 import pickle
 
+from core import constants
 from twtr import utils
 
 
-BASE_DIR = os.path.dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
-HTML_DIR = os.path.join(BASE_DIR, 'html')
-
-
-with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 parsed_chains = utils.parse_chains(chains)
@@ -41,5 +37,5 @@ for counter, chain in parsed_chains.items():
             author=next(author), message=message
         ).replace('\n', '<br>')
 
-with open(os.path.join(HTML_DIR, 'messages.html'), 'w') as f:
+with open(os.path.join(constants.HTML_DIR, 'messages.html'), 'w') as f:
     f.write(html)

### 2016-04-28 run_measures.py

@@ -4,17 +4,15 @@ import pickle
 from spacy.en import English
 from textblob import TextBlob
 
+from core import constants
 from measures import lla, lsm
 from twtr import utils
 
 
-BASE_DIR = os.path.dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
-
 nlp = English()
 
 
-with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 parsed_chains = utils.parse_chains(chains, escape_html=False)

### 2016-04-28 twtr/get_tweets.py

@@ -4,6 +4,8 @@ import sys
 
 import tweepy
 
+from core import constants
+
 
 CONSUMER_KEY = os.environ['TWITTER_CONSUMER_KEY']
 CONSUMER_SECRET = os.environ['TWITTER_CONSUMER_SECRET']
@@ -82,5 +84,5 @@ while len(chains) < 200:
 
     page += 1
 
-with open('tweets.pickle', 'wb') as f:
+with open(os.path.join(constants.DATA_DIR, 'tweets.pickle'), 'wb') as f:
     pickle.dump(chains, f)

### 2016-04-28 twtr/select_tweets.py

@@ -3,8 +3,7 @@ import pickle
 
 from distutils.util import strtobool
 
-
-DATA_DIR = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'data')
+from core import constants
 
 
 def query_yes_no(question, default="yes"):
@@ -16,7 +15,7 @@ def query_yes_no(question, default="yes"):
             print("Please respond with 'y' or 'n'.")
 
 
-with open(os.path.join(DATA_DIR, 'tweets.pickle'), 'rb') as f:
+with open(os.path.join(constants.DATA_DIR, 'tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 keepers = []
@@ -28,5 +27,5 @@ for chain in chains:
     if is_keeper:
         keepers.append(chain)
 
-with open(os.path.join(DATA_DIR, 'selected_tweets.pickle'), 'wb') as f:
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'wb') as f:
     pickle.dump(keepers, f)

### 2016-04-28 twtr/tweets_to_text.py

@@ -1,7 +1,10 @@
+import os
 import pickle
 
+from core import constants
 
-with open('selected_tweets.pickle', 'rb') as f:
+
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
     chains = pickle.load(f)
 
 

### 2016-04-29 core/constants.py
Save classifications

@@ -2,5 +2,5 @@ import os
 
 
 BASE_DIR = BASE_DIR = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))
-DATA_DIR = os.path.join(BASE_DIR, 'twtr', 'data')
+DATA_DIR = os.path.join(BASE_DIR, 'data')
 HTML_DIR = os.path.join(BASE_DIR, 'html')

### 2016-04-29 run_measures.py

@@ -1,5 +1,6 @@
 import os
 import pickle
+import statistics
 
 from spacy.en import English
 from textblob import TextBlob
@@ -17,20 +18,31 @@ with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f
 
 parsed_chains = utils.parse_chains(chains, escape_html=False)
 
+chain_scores = {}
 for chain_id, chain in parsed_chains.items():
     messages_a = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[::2]]
     messages_b = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[1::2]]
+    chain_scores[chain_id] = {}
 
+    lilla_scores = silla_scores = lsm_scores = wv_scores = []
     for counter, message_a in enumerate(messages_a, 1):
         for message_b in messages_b[counter:]:
-            lilla_score = lla.lilla(message_a['textblob'].words, message_b['textblob'].words)
-            silla_score = lla.silla(message_a['spacy'], message_b['spacy'])
-            lsm_score = lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])
-            wv_score = message_a['spacy'].similarity(message_b['spacy'])
+            lilla_scores.append(lla.lilla(message_a['textblob'].words, message_b['textblob'].words))
+            silla_scores.append(lla.silla(message_a['spacy'], message_b['spacy']))
+            lsm_scores.append(lsm.dyad_lsm(message_a['spacy'], message_b['spacy']))
+            wv_scores.append(message_a['spacy'].similarity(message_b['spacy']))
 
     for counter, message_b in enumerate(messages_b, 1):
         for message_a in messages_a[counter:]:
-            lilla_score = lla.lilla(message_a['textblob'].words, message_b['textblob'].words)
-            silla_score = lla.silla(message_a['spacy'], message_b['spacy'])
-            lsm_score = lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])
-            wv_score = message_a['spacy'].similarity(message_b['spacy'])
+            lilla_scores.append(lla.lilla(message_a['textblob'].words, message_b['textblob'].words))
+            silla_scores.append(lla.silla(message_a['spacy'], message_b['spacy']))
+            lsm_scores.append(lsm.dyad_lsm(message_a['spacy'], message_b['spacy']))
[…]

### 2016-04-29 save_classifications.py

@@ -1,0 +1,40 @@
+import argparse
+import csv
+import os
+import pickle
+import statistics
+
+from core import constants
+
+
+def get_means(classifications, category):
+    scores_zip = zip(*[classifier[category] for classifier in classifications['classifiers'].values()])
+    return [statistics.mean(scores) for scores in scores_zip]
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument('infiles', nargs='+', type=argparse.FileType('r'))
+args = parser.parse_args()
+
+classifications = {
+    'classifiers': {},
+    'means': {},
+}
+for classifier, csvfile in enumerate(args.infiles, 1):
+    classifications['classifiers'][classifier] = {
+        'lexical': [],
+        'syntactic': [],
+        'semantic': [],
+    }
+    reader = csv.DictReader(csvfile)
+    for row in reader:
+        classifications['classifiers'][classifier]['lexical'].append(int(row['Lexical']))
+        classifications['classifiers'][classifier]['syntactic'].append(int(row['Syntactic']))
+        classifications['classifiers'][classifier]['semantic'].append(int(row['Semantic']))
+
+classifications['means']['lexical'] = get_means(classifications, 'lexical')
+classifications['means']['syntactic'] = get_means(classifications, 'syntactic')
+classifications['means']['semantic'] = get_means(classifications, 'semantic')
+
+with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'wb') as f:
+    pickle.dump(classifications, f)

### 2016-05-04 papers/asonam2016/paper.tex
Write up results

@@
 \usepackage[style=ieee, backend=biber]{biblatex}
+\usepackage[T1]{fontenc}
 
@@
 	\graphicspath{{img/}}
-	\DeclareGraphicsExtensions{.pdf,.jpg,.png}
+	\DeclareGraphicsExtensions{.pdf,.jpg,.png, .eps}
 \else
@@
  	\graphicspath{{img/}}
-	\DeclareGraphicsExtensions{.pdf,.jpg,.png}
+	\DeclareGraphicsExtensions{.pdf,.jpg,.png, .eps}
 \fi
@@
 %
-%\usepackage{url}
+\usepackage{url}
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 \begin{abstract}
-The Interactive Alignment Model is the prevailing theory of
-[I probably need some help phrasing this].
-In this study we investigate how several linguistic alignment techniques can be used
-to detect mimicry at the lexical, syntactic and semantic levels of the
-Interactive Alignment Model.
+The Interactive Alignment Model is the prevailing theory of linguistic alignment works from a psychological standpoint.
+In this study we investigate how several linguistic alignment techniques can be used to detect mimicry at the lexical, syntactic and semantic levels of the Interactive Alignment Model.
 
@@
 \section{The Interactive Alignment Model}
-The Interactive Alignment Model (IAM) \cite{pickering2004toward} is an attempt to model alignment in
-conversations. It consists of six layers, which with the exception of the top layer, the situation
-model, are all representations of some aspect of speech.
+The Interactive Alignment Model (IAM) \cite{pickering2004toward} is an attempt to model alignment in conversations.
+It consists of six layers, which with the exception of the top layer, the situation model, are all representations of some aspect of speech.
 
@@
 	\item The lexical representation --- the choice of words used
-	\item The phonological representation --- ???
+	\item The phonological representation --- the abstract representation of word sounds
 	\item The phonetic representation --- the sounds of an utterance
@@
 
-The phonological and phonetic representations are not discussed in this paper as they relate purely
-to the sound of speech, representations that do not exist in the written text of online conversations.
+The phonological and phonetic representations are not discussed in this paper as they relate purely to the sound of speech, representations that do not exist in the written text of online conversations.
 
-Further, the situation model is not included as there are currently no measures that can be used for
-finding alignment at the situational level.
+Further, the situation model is not included as there are currently no measures that can be used for finding alignment at the situational level.
 
-The theory states that alignment is automatic, that conversation partners will align their speech 
-towards each other at every level of the model. In addition, alignment "percolates" between layers such
-that increased alignment in one layer will lead to increased alignment in other layers.
+The theory states that alignment is automatic, that conversation partners will align their speech  towards each other at every level of the model.
+In addition, alignment "percolates" between layers such that increased alignment in one layer will lead to increased alignment in other layers.
 
@@
 
+There are many techniques that work at the lexical level, many of which can be re-purposed to be used at the syntactic level by replacing the words with phrase or dependency tree notation.
+One technique was used to represent each IAM layer, and one technique that works outside of the IAM.
+
+The criteria for choosing techniques were:
+
+\begin{itemize}
+	\item Newer techniques were preferred over older ones.
+	\item Availability of a source implementation or simplicity of implementation
+\end{itemize}
+
 \subsection{Local Linguistic Alignment}
-Local Linguistic Alignment (LLA) is a simple,  dual purpose method that can work at both the lexical
-and syntactic layers \cite{wang2014linguistic, xu2015evaluation}.
+Local Linguistic Alignment (LLA) is a simple,  dual purpose method that can work at both the lexical and syntactic layers \cite{wang2014linguistic, xu2015evaluation}.
 
-Lexical Indiscriminate Local Linguistic Alignment (LILLA) works at the lexical layer. It gives the
-probability that a word from the prime document will appear at a particular position in the target 
-document. It is defined as:
+Lexical Indiscriminate Local Linguistic Alignment (LILLA) works at the lexical layer.
+It gives the probability that a word from the prime document will appear at a particular position in the target  document.
+It is defined as:
 
@@
 
-Syntactic Indiscriminate Local Linguistic Alignemnt (SILLA) works at the syntactic layer. It works
-in exactly the same way as LILLA, but instead of comparing words, each sentence is annotated with a
-phrase structure tree, and LLA is run on these instead. As such, it measures the probability of a
-phrase structure subtree in the prime document appearing occurring at a given position in the target
-document.
+Syntactic Indiscriminate Local Linguistic Alignemnt (SILLA) works at the syntactic layer.
+It works in exactly the same way as LILLA, but instead of comparing words, each sentence is annotated with a phrase structure tree, and LLA is run on these instead.
+As such, it measures the probability of a phrase structure subtree in the prime document appearing occurring at a given position in the target document.
 
-\subsection{Hierarchical Alignment Model}
-The Hierarchical Alignment Model (HAM) \cite{doyle2016robust} is ...
-So it finds the most common words, uses these as markers, then looks at how often these markers
-appear.
+\subsection{Word Vectors}
+Word2vec \cite{mikolov2013efficient, mikolov2013distributed} is a machine learning technique that, given a word, tries to predict the two adjacent words.
+Each word is then mapped to vector space and can be directly compared.
+The closer the two word vectors to each other, the more semantically related they are.
 
-\subsection{Word and Document Vectors}
-Word2vec \cite{mikolov2013efficient, mikolov2013distributed} is a machine learning technique that,
-given a word, tries to predict the two adjacent words. Each word is then mapped to vector space
-and can be directly compared. The closer the two word vectors to each other, the more semantically
-related they are.
-
-Doc2vec \cite{le2014distributed} works on the same principle as Word2vec. Here, each word is mapped to
-a unique vector, and each paragraph is also mapped to a vector, which contribute to predicting the next
-word in the paragraph. It can be used with not only paragraphs, but with sentences or entire documents.
-
-[I can't find any pretrained doc2vec models trained on twitter data and don't have the data to do it
-myself so this might end up relegated to future work]
+While word vectors have not been used to measure mimicry before, we posit that it may give good results for finding mimicry as it gets good results in the related field of sentiment analysis and is used to find semantic similarity of texts.
 
 \subsection{Language Style Matching}
-Language Style Matching (LSM) \cite{ireland2010language, ireland2011language}
-is a measure that counts the usage of function words by an interlocutor.
-For each class of function word (e.g., determiners, pronouns, adpositions), the number of words is 
-calculated as a percentage of the total document, which is the score for each class. Scores are 
-calculated between the dyad using a weighted difference, shown below, and these scores averaged to 
-produce a single LSM score for that dyad.
+Language Style Matching (LSM) \cite{ireland2010language, ireland2011language} is a measure that counts the usage of function words by an interlocutor.
+For each class of function word (e.g., determiners, pronouns, adpositions), the number of words is  calculated as a percentage of the total document, which is the score for each class.
+Scores are calculated between the dyad using a weighted difference, shown below, and these scores averaged to produce a single LSM score for that dyad.
 
@@
 \section{Method}
-The dataset consists of 103 dyadic conversations taken from Twitter. Tweets were found via Twitter's 
-search API, using English language and being a reply as criteria. We then work up the chain of tweets 
-until we hit the end, or a third interlocutor is found, at which point the conversation is cut off and 
-kept, as long as there are no fewer than 10 tweets in the conversation. 200 tweets were found using 
-this method. Of these, 62 were removed as they were not true conversations (either monologues or 
-collaborative fiction writing/roleplay). 18 conversations were removed as they had significant amounts 
-of non-English text. 17 conversations involved bots and were also removed.
+The dataset consists of 103 dyadic conversations taken from Twitter.
+Tweets were found via Twitter's  search API, using English language and being a reply as criteria.
+We then work up the chain of tweets  until we hit the end, or a third interlocutor is found, at which point the conversation is cut off and  kept, as long as there are no fewer than 10 tweets in the conversation.
+200 tweets were found using  this method.
+Of these, 62 were removed as they were not true conversations (either monologues or  collaborative fiction writing/roleplay).
+18 conversations were removed as they had significant amounts  of non-English text.
+17 conversations involved bots and were also removed.
 
@@
 
-The dataset is small, which is both an advantage as it is possible to classify the data manually
-and a disadvantage in that the sample size is smaller. We did not actively seek out mimicry by
-targeting our search as it was important to have conversations that would test negatively for mimicry
-as well as positively.
+The dataset is small, which is both an advantage as it is possible to classify the data manually and a disadvantage in that the sample size is smaller.
+We did not actively seek out mimicry by targeting our search as it was important to have conversations that would test negatively for mimicry as well as positively.
 
-The data was classified by three researchers with backgrounds in mimicry independent of the authors of 
-this paper.
-Each  conversation was classified for lexical, syntactic and semantic mimicry on a three point scale 
-where 0 represents no mimicry, 1 represents low levels of mimicry at that layer, and 2 represents high 
-levels of mimicry. Classifications from each author were averaged together to give each conversation
-three scores between 0 and 2.
+The data was classified by three researchers with backgrounds in mimicry independent of the authors of  this paper.
+Each  conversation was classified for lexical, syntactic and semantic mimicry on a three point scale  where 0 represents no mimicry, 1 represents low levels of mimicry at that layer, and 2 represents high  levels of mimicry.
+Classifications from each author were averaged together to give each conversation three scores between 0 and 2.
 
-Each measure was then run against the data such that each message from author A is compared with each 
-message from author B that occurred before the original message.
+Each measure was then run against the data such that each message from author A is compared with each  message from author B that occurred before the original message.
 
-HAM is treated differently as it requires data to be set up in a different way.
-Here we have reused the original implementation, and have formatted the data into tab separated
-values files with each row being a pair of tweets, with an extra TSV file to store user information.
 \footnote{[I could probably make my github repo public and put a link to the code here?]}
@@
 \section{Results}
-Still not sure how to compare everything.
+
+In general, the human classifiers agreed with each other, but the agreement is fairly weak.
+They most strongly agreed on syntactic mimicry, \(r > 0.28, < 0.36, p < 0.004\).
+Additionally there seemed to be more agreement on lexical mimicry than semantic, but p values are too high to make a definitive judgment.
+
+The mean scores from human classifiers also show positive but weak correlation with the scores from their respective techniques.
+Additionally means of all human classifier scores were used as a comparison with LSM.
+These correlations can be seen in Table \ref{scores_techniques}.
+
+\begin{table}[!t]
+\caption{Correlations of Classifier Scores and Techniques}
+\label{scores_techniques}
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{l c c}
+Layer, Technique & r & p \\
+\hline
+Lexical, LILLA & 0.27 & 0.005 \\
+Syntactic, SILLA & 0.19 & 0.057 \\
+Semantic, Word2vec & 0.11 & 0.231 \\
+N/A (mean scores), LSM & 0.16 & 0.111 \\
+\end{tabular}
+\end{table}
+
+To observe the IAM's prediction that increased levels of mimicry on one layer results in a higher probability of mimicry in other adjacent layers, we looked at the correlations between the results of our techniques, in Table \ref{techniques}, and also between the results of the human classifiers, in Table \ref{classifications}.
+
+\begin{table}[!t]
+\caption{Correlations of Techniques}
+\label{techniques}
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{l c c}
+Technique & r & p \\
+\hline
+LILLA, SILLA & 0.26 & 0.007 \\
+LILLA, Word2vec & -0.31 & 0.002 \\
+SILLA, Word2vec & -0.81 & < 0.001
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\caption{Correlations of Human Classifications}
+\label{classifications}
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{l c c}
+Layer & r & p \\
+\hline
+Lexical, Syntactic & 0.57 & < 0.001 \\
+Lexical, Semantic & 0.33 & < 0.001 \\
+Syntactic, Semantic & 0.28 & 0.005
+\end{tabular}
+\end{table}
 
@@
 
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-
 \section{Discussion}

### 2016-05-04 export_to_ham.py

@@ -1,62 +1,0 @@
-import csv
-import os
-import pickle
-
-from core import constants
-from twtr import utils
-
-
-with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-
-def build_user_tsv():
-    fieldnames = ['uid', 'screenname', 'verified', 'numtweets', 'numfriends', 'numfollowers', 'numlistsin',
-                  'numfavoritesgiven', 'creationyear', 'creationmonth', 'creationdate']
-    for conversation_id, chain in enumerate(chains, 1):
-        authors = {status.author for status in chain}
-        with open(os.path.join(constants.DATA_DIR, 'ham', str(conversation_id).zfill(3) + '_users.tsv'), 'w') as f:
-            writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
-            for author in authors:
-                writer.writerow({
-                    'uid': author.id_str,
-                    'screenname': author.screen_name,
-                    'verified': author.verified,
-                    'numtweets': author.statuses_count,
-                    'numfriends': author.friends_count,
-                    'numfollowers': author.followers_count,
-                    'numlistsin': author.listed_count,
-                    'numfavoritesgiven': author.favourites_count,
-                    'creationyear': author.created_at.year,
-                    'creationmonth': author.created_at.month,
-                    'creationdate': author.created_at.day,
-                })
-
-
-def build_status_tsv():
-    fieldnames = ['msgid', 'msguser', 'msgtext', 'replyid', 'replyuser', 'replytext']
-
-    for conversation_id, chain in enumerate(chains, 1):
-        with open(os.path.join(constants.DATA_DIR, 'ham', str(conversation_id).zfill(3) + '.tsv'), 'w') as f:
-            writer = csv.DictWriter(f, dialect='excel-tab', fieldnames=fieldnames)
-            previous_status = None
-            for counter, status in enumerate(chain):
-                if counter == 0:
-                    previous_status = status
-                    continue
-
-                assert status.in_reply_to_status_id_str == previous_status.id_str
-
-                writer.writerow({
-                    'msgid': status.id_str,
-                    'msguser': status.author.id_str,
-                    'msgtext': utils.format_message(status.text, is_ham=True),
-                    'replyid': previous_status.id_str,
-                    'replyuser': previous_status.author.id_str,
[…]

### 2016-05-04 iam_correlations.py

@@ -1,0 +1,30 @@
+import itertools
+import os
+import pickle
+
+from scipy import stats
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as c, \
+        open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'rb') as s:
+    classifications = pickle.load(c)
+    scores = pickle.load(s)
+
+
+scores_dict = {}
+for measure in ['lilla', 'silla', 'wv']:
+    scores_dict[measure] = [chain_scores[measure] for chain_scores in scores.values()]
+
+for measure_a, measure_b in itertools.combinations(scores_dict.keys(), 2):
+    print(measure_a, 'vs', measure_b)
+    r, p = stats.pearsonr(scores_dict[measure_a], scores_dict[measure_b])
+    print('r={r}, p={p:.20f}'.format(r=r, p=p))
+
+print()
+
+for category_a, category_b in itertools.combinations(classifications['means'].keys(), 2):
+    print(category_a, 'vs', category_b)
+    r, p = stats.pearsonr(classifications['means'][category_a], classifications['means'][category_b])
+    print('r={r}, p={p:.20f}'.format(r=r, p=p))

### 2016-05-04 run_measures.py

@@ -11,6 +11,7 @@ from twtr import utils
 
 
 nlp = English()
+nlp.vocab.load_vectors(os.path.join(constants.DATA_DIR, 'word2vec_twitter_model.bin'))
 
 
 with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
@@ -24,20 +25,24 @@ for chain_id, chain in parsed_chains.items():
     messages_b = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[1::2]]
     chain_scores[chain_id] = {}
 
-    lilla_scores = silla_scores = lsm_scores = wv_scores = []
+    lilla_scores = []
+    silla_scores = []
+    lsm_scores = []
+    wv_scores = []
+
     for counter, message_a in enumerate(messages_a, 1):
         for message_b in messages_b[counter:]:
-            lilla_scores.append(lla.lilla(message_a['textblob'].words, message_b['textblob'].words))
-            silla_scores.append(lla.silla(message_a['spacy'], message_b['spacy']))
-            lsm_scores.append(lsm.dyad_lsm(message_a['spacy'], message_b['spacy']))
-            wv_scores.append(message_a['spacy'].similarity(message_b['spacy']))
+            lilla_scores.append(float(lla.lilla(message_a['textblob'].words, message_b['textblob'].words)))
+            silla_scores.append(float(lla.silla(message_a['spacy'], message_b['spacy'])))
+            lsm_scores.append(float(lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])))
+            wv_scores.append(float(message_a['spacy'].similarity(message_b['spacy'])))
 
     for counter, message_b in enumerate(messages_b, 1):
         for message_a in messages_a[counter:]:
-            lilla_scores.append(lla.lilla(message_a['textblob'].words, message_b['textblob'].words))
-            silla_scores.append(lla.silla(message_a['spacy'], message_b['spacy']))
-            lsm_scores.append(lsm.dyad_lsm(message_a['spacy'], message_b['spacy']))
-            wv_scores.append(message_a['spacy'].similarity(message_b['spacy']))
+            lilla_scores.append(float(lla.lilla(message_a['textblob'].words, message_b['textblob'].words)))
+            silla_scores.append(float(lla.silla(message_a['spacy'], message_b['spacy'])))
[…]

### 2016-05-04 run_scores.py

@@ -1,0 +1,39 @@
+import os
+import pickle
+import statistics
+
+from scipy import stats
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as f:
+    classifications = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'rb') as f:
+    scores = pickle.load(f)
+
+lexical_scores = classifications['means']['lexical']
+syntactic_scores = classifications['means']['syntactic']
+semantic_scores = classifications['means']['semantic']
+mean_scores = [statistics.mean(scores) for scores in zip(*[lexical_scores, syntactic_scores, semantic_scores])]
+
+lilla_scores = [score['lilla'] for score in scores.values()]
+silla_scores = [score['silla'] for score in scores.values()]
+wv_scores = [score['wv'] for score in scores.values()]
+lsm_scores = [score['lsm'] for score in scores.values()]
+
+r, p = stats.pearsonr(lexical_scores, lilla_scores)
+print('Lexical vs LILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(syntactic_scores, silla_scores)
+print('Syntactic vs SILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(semantic_scores, wv_scores)
+print('Semantic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(mean_scores, lsm_scores)
+print('Mean vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(lexical_scores, lsm_scores)
+print('Lexical vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))

### 2016-05-06 papers/asonam2016/paper.tex
Finish up paper

@@
 \usepackage[T1]{fontenc}
+\usepackage{array}
 
@@
 % http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
 
@@
 
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
 \usepackage{url}
@@
 % Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
 
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
 \author{\IEEEauthorblockN{Tom Carrick, Awais Rashid, Paul J Taylor}
@@
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
 \begin{abstract}
-The Interactive Alignment Model is the prevailing theory of linguistic alignment works from a psychological standpoint.
-In this study we investigate how several linguistic alignment techniques can be used to detect mimicry at the lexical, syntactic and semantic levels of the Interactive Alignment Model.
+A number of computational techniques have been proposed that aim to detect mimicry in online conversations.
+In this paper, we investigate how well these reflect the prevailing cognitive science model, i.e.
+the Interactive Alignment Model.
+We evaluate Local Linguistic Alignment, word vectors, and Language Style Matching and show that these measures tend to show the features we expect to see in the IAM, but significantly fall short of the work of human classifiers on the same data set.
+This reflects the need for substantial additional research on computational techniques to detect mimicry in online conversations.
+We suggest further work needed to measure these techniques and others more accurately.
 
-We show that [something].
 \end{abstract}
@@
 
-Mimicry in online conversations is an important and active area of research.
-Humans tend to mimic each other in many areas, such as speech \cite{levelt1982surface, bock1986syntactic, bock1989closed, garrod1987saying}, physical actions \cite{bernieri1988coordinated} and written text \cite{danescu2011chameleons, scissors2008linguistic}.
+When interacting with others, humans show a tendency to mimic one another's behavior, including speech \cite{levelt1982surface, bock1986syntactic, bock1989closed, garrod1987saying}, physical actions \cite{bernieri1988coordinated} and written text \cite{danescu2011chameleons, scissors2008linguistic}.
+Existing research has shown that people who mimic each other's language have more successful outcomes in joint tasks \cite{richardson2014language}, and that decreasing mimicry can be an indicator of deception \cite{taylor2013detecting}.
+Hence, detection of mimicry can be a valuable indicator in dyadic conversations as well as group dynamics in collaborative settings \cite{scissors2009cmc}.
+Potential applications include promoting cooperation, detecting malintent, and identifying leaders.
 
-Existing research has shown that people who mimic each other’s language have more successful outcomes in joint tasks \cite{maddux2008chameleons}.
-Hence, detection of mimicry can be a valuable indicator in understanding group dynamics in collaborative settings.
-It can also play a role in other application areas, e.g., for detection of insider threats \cite{taylor2013detecting}.
+There are a number of measures designed to capture mimicry in text, and some efforts have been made to compare and trial some of these techniques \cite{xu2015evaluation}.
+However, few techniques are grounded in what cognitive  science knows about how mimicry works within humans.
+That is to say, few of the existing techniques are designed to measure the linguistic components of mimicry as specified by contemporary models from cognitive science.
 
-There are a number of measures designed to capture mimicry in text, and some efforts have been made to compare and trial these techniques.
-However, few of these techniques are grounded in what cognitive  science knows about how mimicry works within humans.
-
-This paper addresses this limitation by contrasting how well existing linguistic analysis techniques work to detect mimicry in relation to the Interactive Alignment Model.
-Further, we also consider some existing techniques that have not previously been used to detect mimicry and discuss their viability.
+This paper addresses this limitation by contrasting how well existing linguistic analysis techniques work to detect mimicry in relation to a prominent model of human interpersonal mimicry, the Interactive Alignment Model.
+Further, we consider some existing techniques that have not previously been used to detect mimicry and discuss their viability.
 The novel contributions of this paper are as follows:
 \begin{itemize}
-	\item We compare existing mimicry detection techniques and how they map to the Interactive Alignment Model 
-	\item  We evaluate techniques that have not been used for mimicry detection before and discuss their feasibility in this regard.
-	\item On the basis of our analysis, we posit that hybrid techniques, composing multiple measures, may offer a more holistic approach for mimicry detection.
+	\item We compare two existing mimicry detection techniques and how they map to the Interactive Alignment Model, Local Linguistic Alignment \cite{wang2014linguistic} and Language Style Matching \cite{ireland2010language}.
+	\item  We evaluate and discuss the feasibility of using word vectors \cite{mikolov2013efficient} to measure semantic mimicry.
+	\item We find how one measure, Language Style Matching \cite{ireland2010language}, that does not appear to fit into the model, may nevertheless have a place in the model.
 \end{itemize}
 
-Existing work has compared several methods, e.g., \cite{xu2015evaluation}, including some discussed in this paper.
-However, such works do not aim to contrast the effectiveness of the measures with regards to cognitive models such as the Interactive Alignment Model.
-To our knowledge, our work is the first to undertake such a comparison.
-
 The rest of this paper is structured as follows.
-In Section II, we briefly introduce the Interactive Alignment Model - the psychological model of mimicry against which we test our techniques.
-Section III provides a brief introduction to each measure tested in the paper, and defines the layer of the IAM (if any) in which the measure resides.
+In Section II, we briefly introduce the Interactive Alignment Model.
+Section III provides a brief introduction to each measure tested in the paper, and defines the layer of the IAM (if any) in which the measure appears to reside.
 Section IV describes the data set used in our analysis.
-Section V presents the results of our analysis and highlights the importance of composing multiple measures.
+Section V presents the results of our analysis and highlights how current techniques fit into the IAM in practice.
 Finally, Section VI concludes the paper and identifies directions for future work.
@@
 \section{The Interactive Alignment Model}
-The Interactive Alignment Model (IAM) \cite{pickering2004toward} is an attempt to model alignment in conversations.
-It consists of six layers, which with the exception of the top layer, the situation model, are all representations of some aspect of speech.
+The Interactive Alignment Model (IAM) \cite{pickering2004toward}, shown in Fig.
+\ref{iam} is an attempt to model alignment in conversations.
+It consists of six layers, which with the exception of the top layer, the situation model, are all representations of some aspect of speech, as understood by each speaker within an interaction.
+In basic terms:
 
@@
 
-The phonological and phonetic representations are not discussed in this paper as they relate purely to the sound of speech, representations that do not exist in the written text of online conversations.
-
-Further, the situation model is not included as there are currently no measures that can be used for finding alignment at the situational level.
-
 The theory states that alignment is automatic, that conversation partners will align their speech  towards each other at every level of the model.
@@
 
+The phonological and phonetic representations are not discussed in this paper as they relate purely to the sound of speech, representations that do not exist in the written text of online conversations.
+Further, the situation model is not included as there are currently no measures that can be used for finding alignment at the situational level.
+
 \begin{figure*}
 \caption{The interactive alignment model}
+\label{iam}
 \includegraphics[width=\textwidth]{iam}
@@
 
-There are many techniques that work at the lexical level, many of which can be re-purposed to be used at the syntactic level by replacing the words with phrase or dependency tree notation.
-One technique was used to represent each IAM layer, and one technique that works outside of the IAM.
+There are many techniques for finding mimicry, but few of them specifically target any layer of the IAM.
+We chose one measure for each layer, as well as Language Style Matching to have a technique that could fit into the lexical layer, or could be seen to work outside of the IAM.
 
-The criteria for choosing techniques were:
-
-\begin{itemize}
-	\item Newer techniques were preferred over older ones.
-	\item Availability of a source implementation or simplicity of implementation
-\end{itemize}
+Techniques were chosen mostly to try to fit into a layer of the IAM.
+Simplicity of implementation and access to source implementations was also a factor, and modern techniques were favoured over older ones.
 
@@
 Local Linguistic Alignment (LLA) is a simple, dual purpose method that can work at both the lexical and syntactic layers \cite{wang2014linguistic, xu2015evaluation}.
+LLA was chosen specifically as it was the only measure the authors could find where it is explicitly stated to work at the lexical and syntactic layers.
 
@@
 \subsection{Word Vectors}
-Word2vec \cite{mikolov2013efficient, mikolov2013distributed} is a machine learning technique that, given a word, tries to predict the two adjacent words.
+Word2vec \cite{mikolov2013efficient} is a machine learning technique that, given a word, tries to predict the two adjacent words.
 Each word is then mapped to vector space and can be directly compared.
@@
 
-While word vectors have not been used to measure mimicry before, we posit that it may give good results for finding mimicry as it gets good results in the related field of sentiment analysis and is used to find semantic similarity of texts.
+While word vectors have not been used to measure mimicry before, we posit that it may give good results for finding mimicry as it is used for finding semantic similarity in text, we would expect it to also find semantic mimicry.
 
 \subsection{Language Style Matching}
-Language Style Matching (LSM) \cite{ireland2010language, ireland2011language} is a measure that counts the usage of function words by an interlocutor.
+Language Style Matching (LSM) \cite{ireland2010language} is a measure that counts the usage of function words by an interlocutor.
 For each class of function word (e.g., determiners, pronouns, adpositions), the number of words is  calculated as a percentage of the total document, which is the score for each class.
@@
 \section{Method}
-The dataset consists of 103 dyadic conversations taken from Twitter.
+The data set consists of 103 dyadic conversations taken from Twitter.
 Tweets were found via Twitter's  search API, using English language and being a reply as criteria.
@@
 
-The dataset is small, which is both an advantage as it is possible to classify the data manually and a disadvantage in that the sample size is smaller.
+Twitter was chosen as it is relatively easy to extract data from, and the short utterance and conversation length make it more reasonable for humans to classify, as with longer texts they may find more difficulty in keeping less recent utterances in mind while evaluating more recent ones.
+
+The data set is small, which is both an advantage as it is possible to classify the data manually and a disadvantage in that the sample size is smaller.
 We did not actively seek out mimicry by targeting our search as it was important to have conversations that would test negatively for mimicry as well as positively.
@@
 Each measure was then run against the data such that each message from author A is compared with each  message from author B that occurred before the original message.
+\footnote{Source code available at \url{https://github.com/knyghty/linguistic-analysis}.}
 
-\footnote{[I could probably make my github repo public and put a link to the code here?]}
+\section{Results and Disucssion}
 
-\section{Results}
+\begin{table}[!t]
+\caption{Correlations of Classifiers With Each Other}
+\label{classifiers}
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{l | c c | c c | c c}
+Pair & \multicolumn{2}{|c|}{Lexical} & \multicolumn{2}{|c|}{Syntactic} & \multicolumn{2}{|c}{Semantic} \\
+ & r & p & r & p & r & p \\
+\hline
+AB & 0.28 & 0.779 & 0.36 & < 0.001 & 0.19 & 0.058 \\
+AC & 0.32 & 0.001 & 0.35 & < 0.001 & 0.12 & 0.220 \\
+BC & -0.02 & 0.863 & 0.29 & 0.003 & 0.10 & 0.312
+\end{tabular}
+\end{table}
 
+Table \ref{classifiers} shows the correlations between the scores of each pair of classifiers.
 In general, the human classifiers agreed with each other, but the agreement is fairly weak.
-They most strongly agreed on syntactic mimicry, \(r > 0.28, < 0.36, p < 0.004\).
+They most strongly agreed on syntactic mimicry.
 Additionally there seemed to be more agreement on lexical mimicry than semantic, but p values are too high to make a definitive judgment.
-
-The mean scores from human classifiers also show positive but weak correlation with the scores from their respective techniques.
-Additionally means of all human classifier scores were used as a comparison with LSM.
-These correlations can be seen in Table \ref{scores_techniques}.
 
@@
 Semantic, Word2vec & 0.11 & 0.231 \\
-N/A (mean scores), LSM & 0.16 & 0.111 \\
+Lexical, LSM & 0.14 & 0.158 \\
+Syntactic, LSM & 0.31 & 0.002 \\
+Semantic, LSM & -0.13 & 0.202 \\
+N/A (mean scores), LSM & 0.16 & 0.111
 \end{tabular}
@@
 
-To observe the IAM's prediction that increased levels of mimicry on one layer results in a higher probability of mimicry in other adjacent layers, we looked at the correlations between the results of our techniques, in Table \ref{techniques}, and also between the results of the human classifiers, in Table \ref{classifications}.
+Table \ref{scores_techniques} shows the correlations between the mean scores from the human classifiers with the measure they should fall into.
+Additionally means of all human classifier scores were used as a comparison with LSM, and LSM was compared with all other scores, to see where it best fits within the IAM.
+We see that scores from human classifiers show positive but weak correlation with the scores from their respective techniques.
+Additionally, LSM has a much better correlation with our syntactic scores than any other.
+Despite operating at the word level, LSM appears to be more of a syntactic measure than a lexical measure.
+This makes some sense when considering that choosing different function words may force a change of syntax.
 
@@
 
+Table \ref{techniques} shows the correlations of the computational methods with each other, to observe the IAM's prediction that increased levels of mimicry on one layer results in a higher probability of mimicry in other adjacent layers.
+The comparison of LILLA and SILLA is quite promising, however the strong negative correlations when word vectors are involved are both concerning and interesting, as this is the opposite of what we expect.
+
 \begin{table}[!t]
@@
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
+Table \ref{classifications} shares the same idea, but compares the human classifiers' lexical, syntactic and semantic scores with each other.
+Here, the results are much closer to what we expect, with moderate positive correlations between all layers.
+The contrast with the word vector results from Table \ref{techniques} suggest that word vectors may not be a good solution for finding semantic mimicry, but doesn't explain the strong negative correlation between SILLA and Word2vec.
+The strong correlation between human classifiers' lexical and syntactic scores compared with the weaker correlation between LILLA and SILLA could suggest that humans are better suited for this task.
 
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
+As results involving the semantic layer generally lead to lower levels of correlation, it could be argued that discerning semantic mimicry is a harder task than for the lexical and syntactic layers.
+However, it should be noted that there is still a weak to moderate positive correlation.
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-\section{Discussion}
-Discussion
+Even defining semantic mimicry was found to be a difficult task.
+It seems to make little sense to say that semantic mimicry is present where the same subject is discussed, as there are few situations where interlocutors will have a conversation about different things at the same time.
+It also makes little sense to define it as agreement with the other interaction partner, as agreement could be natural, rather than evidence of mimicry.
+Instead, we defined semantic mimicry as the people in the conversation communicating using similar concepts.
+This seems to be difficult for humans to analyse, especially from short twitter conversations, and could help to explain why computational methods also find this task difficult.
 
 \section{Conclusion and Future Work}
-The conclusion goes here.
-Zelig \cite{jones2014finding}
 
-% use section* for acknowledgment
+We have presented some initial findings from our study into mimicry in online conversations.
+We have found that current computational methods are not especially good at finding mimicry in accordance with the Interactive Alignment Model, and that human experts currently seem to do a somewhat better job.
+
+Our results further show support for the IAM's theory that mimicry in one layer increases the chance of mimicry in the other layers.
+
+More research is needed, particularly in the methods used to detect mimicry by computational analysis.
+There are many more measures, such as the Hierarchical Alignment Model \cite{doyle2016robust}, Zelig \cite{jones2014finding} and RepDecay \cite{reitter2006computational}, some of which should fit neatly into the lexical and syntactic layers, and some that do not have any basis in the IAM.
+Our data set is small, and using a larger data set, ideally with a greater number of human classifiers would be useful for a more extensive investigation of the phenomenon highlighted in this paper.
+
+More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently, running the measure on all utterances of each pair, rather than averaging the similarity over each pair of messages.
+More research in general is suggested in finding ways to capture mimicry at the semantic layer, and so far there is very little work looking at alignment at the situation layer.
+
 \section*{Acknowledgment}
-This research is funded by the Engineering and Social Sciences (ESRC) Centre for Behavioural and Social Science Approaches to Security (CREST).
+This research is funded by the Engineering and Social Sciences (ESRC) Centre for Research and Evidence on Security Threats (CREST).
 

### 2016-05-06 run_scores.py

@@ -37,3 +37,9 @@ print('Mean vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))
 
 r, p = stats.pearsonr(lexical_scores, lsm_scores)
 print('Lexical vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(syntactic_scores, lsm_scores)
+print('Syntactic vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(semantic_scores, lsm_scores)
+print('Semantic vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))

### 2016-05-11 papers/asonam2016/short.tex
Few more experiments

--- 2016-05-06 papers/asonam2016/paper.tex
@@
 Syntactic, SILLA & 0.19 & 0.057 \\
-Semantic, Word2vec & 0.11 & 0.231 \\
+Semantic, Word2vec & 0.13 & 0.178 \\
 Lexical, LSM & 0.14 & 0.158 \\
@@
 LILLA, SILLA & 0.26 & 0.007 \\
-LILLA, Word2vec & -0.31 & 0.002 \\
-SILLA, Word2vec & -0.81 & < 0.001
+LILLA, Word2vec & -0.30 & 0.005 \\
+SILLA, Word2vec & -0.82 & < 0.001
 \end{tabular}
@@
 
-More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently, running the measure on all utterances of each pair, rather than averaging the similarity over each pair of messages.
+More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently or experimenting with different models.
 More research in general is suggested in finding ways to capture mimicry at the semantic layer, and so far there is very little work looking at alignment at the situation layer.

### 2016-05-11 run_measures.py

@@ -11,7 +11,7 @@ from twtr import utils
 
 
 nlp = English()
-nlp.vocab.load_vectors(os.path.join(constants.DATA_DIR, 'word2vec_twitter_model.bin'))
+# nlp.vocab.load_vectors(os.path.join(constants.DATA_DIR, 'word2vec_twitter_model.bin'))
 
 
 with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
@@ -44,10 +44,14 @@ for chain_id, chain in parsed_chains.items():
             lsm_scores.append(float(lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])))
             wv_scores.append(float(message_a['spacy'].similarity(message_b['spacy'])))
 
+    spacy_a = nlp('\n'.join(chain[::2]))
+    spacy_b = nlp('\n'.join(chain[1::2]))
+
     chain_scores[chain_id]['lilla'] = statistics.mean(lilla_scores)
     chain_scores[chain_id]['silla'] = statistics.mean(silla_scores)
     chain_scores[chain_id]['lsm'] = statistics.mean(lsm_scores)
     chain_scores[chain_id]['wv'] = statistics.mean(wv_scores)
+    chain_scores[chain_id]['wv_conversation'] = spacy_a.similarity(spacy_b)
 
 with open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'wb') as f:
     pickle.dump(chain_scores, f)

### 2016-05-11 run_scores.py

@@ -21,7 +21,9 @@ mean_scores = [statistics.mean(scores) for scores in zip(*[lexical_scores, synta
 lilla_scores = [score['lilla'] for score in scores.values()]
 silla_scores = [score['silla'] for score in scores.values()]
 wv_scores = [score['wv'] for score in scores.values()]
+wv_conversation_scores = [score['wv_conversation'] for score in scores.values()]
 lsm_scores = [score['lsm'] for score in scores.values()]
+
 
 r, p = stats.pearsonr(lexical_scores, lilla_scores)
 print('Lexical vs LILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
@@ -31,6 +33,18 @@ print('Syntactic vs SILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
 
 r, p = stats.pearsonr(semantic_scores, wv_scores)
 print('Semantic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(lexical_scores, wv_scores)
+print('Lexical vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(syntactic_scores, wv_scores)
+print('Syntactic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(mean_scores, wv_scores)
+print('Mean vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(semantic_scores, wv_conversation_scores)
+print('Semantic vs Word2vec (conversation): r={r}, p={p:.20f}'.format(r=r, p=p))
 
 r, p = stats.pearsonr(mean_scores, lsm_scores)
 print('Mean vs LSM: r={r}, p={p:.20f}'.format(r=r, p=p))

### 2016-07-24 papers/asonam2016/paper.tex
Hopefully final version of ASONAM paper

@@
 \usepackage{array}
+\usepackage{url}
+\usepackage{eso-pic}
 
@@
 
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% correct bad hyphenation here
 \hyphenation{op-tical net-works semi-conduc-tor}
@@
 \begin{document}
+
+\IEEEoverridecommandlockouts 
+\IEEEpubid{\begin{minipage}{\textwidth}\ \\[30pt] \\\textbf{IEEE/ACM ASONAM 2016, August 18-21, 2016, San Francisco, CA, USA\\ 978-1-5090-2846-7/16/\$31.00\copyright2016 IEEE} \end{minipage}}
+
+\AddToShipoutPictureBG*{ 
+\AtPageUpperLeft{ 
+\setlength\unitlength{1in} 
+\hspace*{\dimexpr0.5\paperwidth\relax}
+\makebox(0,-0.75)[c]{\textbf{2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM)}}}}
+
 \title{Mimicry in Online Conversations: An Exploratory Study of Linguistic Analysis Techniques}
-
 \author{\IEEEauthorblockN{Tom Carrick, Awais Rashid, Paul J Taylor}
@@
 However, few techniques are grounded in what cognitive science knows about how mimicry works within humans.
-That is to say, few of the existing techniques are designed to measure the linguistic components of mimicry as specified by contemporary models from cognitive science.
+That is to say, few of the existing techniques are designed to measure the linguistic components of verbal mimicry as specified by contemporary models from cognitive science.
 
@@
 \section{The Interactive Alignment Model}
-The Interactive Alignment Model (IAM) \cite{pickering2004toward}, shown in Fig.
-\ref{iam} is an attempt to model alignment in conversations.
-It consists of six layers, which with the exception of the top layer, the situation model, are all representations of some aspect of speech, as understood by each speaker within an interaction.
-In basic terms:
+In order to achieve conversation, two or more interactants must work together to establish a joint understanding of what they are talking about.
+The Interactive Alignment Model (IAM) \cite{pickering2004toward, garrod2004conversation}, shown in Fig.
+\ref{iam} is an attempt to model such alignment as it occurs over time in conversations.
+It consists of six layers, which with the exception of the top layer, the situation model, are all representations of different linguistic levels at the same time, as understood by each speaker within an interaction.
+In basic terms, these levels are:
 
@@
 	\item The situation model --- a representation of the situation being discussed
-	\item The semantic representation --- the meaning of the utterance
+	\item The semantic representation --- the meaning of the utterance in terms of what it stands to convey.
 	\item The syntactic representation --- the sentence structure
@@
 
-The theory states that alignment is automatic, that conversation partners will align their speech  towards each other at every level of the model.
-In addition, alignment "percolates" between layers such that increased alignment in one layer will lead to increased alignment in other layers.
+The theory states that alignment is automatic and that conversation partners will 'interactively align' their speech  towards each other at every level of the model.
+The observable behavior of such alignment is greater mimicry at each layer.
+
+The IAM also postulates how such alignment emerges over time.
+It suggests that alignment 'percolates' between layers such that increased alignment in one layer will lead to increased alignment in other layers.
+For example, tightening the semantic representation will naturally restrict the number of words and syntactic structures that can be used to convey that meaning.
+Similarly, particular word choices may shape the kinds of semantic representations that become prominent.
+In short, alignment at one level enables a listener to fill in the gaps and appropriately mimic at another level.
 
@@
 \subsection{Word Vectors}
-Word2vec \cite{mikolov2013efficient} is a machine learning technique that, given a word, tries to predict the two adjacent words.
+Word2vec \cite{mikolov2013efficient, mikolov2013distributed} is a machine learning technique that, given a word, tries to predict the two adjacent words.
 Each word is then mapped to vector space and can be directly compared.
@@
 \subsection{Language Style Matching}
-Language Style Matching (LSM) \cite{ireland2010language} is a measure that counts the usage of function words by an interlocutor.
+Language Style Matching (LSM) \cite{ireland2010language, ireland2011language} is a measure that counts the usage of function words by an interlocutor.
 For each class of function word (e.g., determiners, pronouns, adpositions), the number of words is  calculated as a percentage of the total document, which is the score for each class.
@@
 
-More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently, running the measure on all utterances of each pair, rather than averaging the similarity over each pair of messages.
+More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently or experimenting with differently trained models.
 More research in general is suggested in finding ways to capture mimicry at the semantic layer, and so far there is very little work looking at alignment at the situation layer.
@@
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
 \printbibliography

### 2016-10-10 classifier_correlation.py
Rejiggy

@@ -1,31 +1,0 @@
-import itertools
-import os
-import pickle
-
-from scipy import stats
-
-from core import constants
-
-
-with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as f:
-    classifications = pickle.load(f)
-
-pairs = itertools.combinations(classifications['classifiers'].keys(), 2)
-
-for classifier_a, classifier_b in pairs:
-    print('Classifiers', classifier_a, 'and', classifier_b)
-
-    lexical_a = classifications['classifiers'][classifier_a]['lexical']
-    lexical_b = classifications['classifiers'][classifier_b]['lexical']
-    r, p = stats.pearsonr(lexical_a, lexical_b)
-    print('Lexical: r={r}, p={p}'.format(r=r, p=p))
-
-    syntactic_a = classifications['classifiers'][classifier_a]['syntactic']
-    syntactic_b = classifications['classifiers'][classifier_b]['syntactic']
-    r, p = stats.pearsonr(syntactic_a, syntactic_b)
-    print('Syntactic: r={r}, p={p}'.format(r=r, p=p))
-
-    semantic_a = classifications['classifiers'][classifier_a]['semantic']
-    semantic_b = classifications['classifiers'][classifier_b]['semantic']
-    r, p = stats.pearsonr(semantic_a, semantic_b)
-    print('Semantic: r={r}, p={p}'.format(r=r, p=p))

### 2016-10-10 core/constants.py

@@ -1,6 +1,0 @@
-import os
-
-
-BASE_DIR = BASE_DIR = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))
-DATA_DIR = os.path.join(BASE_DIR, 'data')
-HTML_DIR = os.path.join(BASE_DIR, 'html')

### 2016-10-10 generate_csv.py

@@ -1,11 +1,0 @@
-import csv
-import os
-
-from core import constants
-
-
-with open(os.path.join(constants.HTML_DIR, 'classifications.csv'), 'w') as csvfile:
-    writer = csv.writer(csvfile)
-    writer.writerow(['', 'Lexical', 'Syntactic', 'Semantic'])
-    for row in range(103):
-        writer.writerow(['Conversation {counter}'.format(counter=row + 1), '', '', ''])

### 2016-10-10 generate_data_csv.py

@@ -1,25 +1,0 @@
-import csv
-import itertools
-import os
-import pickle
-
-from core import constants
-from twtr import utils
-
-
-with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-parsed_chains = utils.parse_chains(chains)
-
-with open(os.path.join(constants.DATA_DIR, 'data.csv'), 'w') as csvfile:
-    writer = csv.writer(csvfile)
-    writer.writerow(['Text'])
-    for chain in parsed_chains.values():
-        row = ''
-        author = itertools.cycle('AB')
-        for message in chain:
-            row += '<p><strong>{author}</strong>: {message}</p>'.format(
-                author=next(author), message=message
-            ).replace('\n', '<br>')
-        writer.writerow([row])

### 2016-10-10 generate_html.py

@@ -1,41 +1,0 @@
-import itertools
-import os
-import pickle
-
-from core import constants
-from twtr import utils
-
-
-with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-parsed_chains = utils.parse_chains(chains)
-
-html = """
-<meta charset="utf-8">
-<title>Messages to classify</title>
-<style>
-  @font-face {
-    font-family: 'Symbola';
-    src: url('Symbola.ttf') format('truetype');
-    text-decoration: none;
-    font-style: normal;
-  }
-  body {
-    font-family: 'Symbola', sans-serif;
-    line-height: 1;
-    font-size: 24px;
-  }
-</style>
-"""
-
-for counter, chain in parsed_chains.items():
-    html += '<h1>Conversation {counter}</h1>'.format(counter=counter + 1)
-    author = itertools.cycle('AB')
-    for message in chain:
-        html += '<p><strong>{author}</strong>: {message}</p>'.format(
-            author=next(author), message=message
-        ).replace('\n', '<br>')
-
-with open(os.path.join(constants.HTML_DIR, 'messages.html'), 'w') as f:
-    f.write(html)

### 2016-10-10 iam_correlations.py

@@ -1,30 +1,0 @@
-import itertools
-import os
-import pickle
-
-from scipy import stats
-
-from core import constants
-
-
-with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as c, \
-        open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'rb') as s:
-    classifications = pickle.load(c)
-    scores = pickle.load(s)
-
-
-scores_dict = {}
-for measure in ['lsm', 'lilla', 'silla', 'wv']:
-    scores_dict[measure] = [chain_scores[measure] for chain_scores in scores.values()]
-
-for measure_a, measure_b in itertools.combinations(scores_dict.keys(), 2):
-    print(measure_a, 'vs', measure_b)
-    r, p = stats.pearsonr(scores_dict[measure_a], scores_dict[measure_b])
-    print('r={r}, p={p:.20f}'.format(r=r, p=p))
-
-print()
-
-for category_a, category_b in itertools.combinations(classifications['means'].keys(), 2):
-    print(category_a, 'vs', category_b)
-    r, p = stats.pearsonr(classifications['means'][category_a], classifications['means'][category_b])
-    print('r={r}, p={p:.20f}'.format(r=r, p=p))

### 2016-10-10 measures/deps.py

@@ -1,7 +1,0 @@
-def subtrees(doc):
-    deps = []
-    for word in doc:
-        children = list(word.children)
-        if len(children):
-            deps.append((word.dep, [child.dep for child in children]))
-    return deps

### 2016-10-10 measures/liwc.py

@@ -1,587 +1,0 @@
-LIWC_DATA = {
-    "adverbs": {
-        "about",
-        "absolutely",
-        "actually",
-        "again",
-        "also",
-        "anyway*",
-        "anywhere",
-        "apparently",
-        "around",
-        "back",
-        "basically",
-        "beyond",
-        "clearly",
-        "completely",
-        "constantly",
-        "definitely",
-        "especially",
-        "even",
-        "eventually",
-        "ever",
-        "frequently",
-        "generally",
-        "here",
-        "heres",
-        "here's",
-        "hopefully",
-        "how",
-        "however",
-        "immediately",
-        "instead",
-        "just",
-        "lately",
-        "maybe",
-        "mostly",
-        "nearly",
-        "now",
-        "often",
-        "only",
-        "perhaps",
-        "primarily",
-        "probably",
-        "push*",
-        "quick*",
-        "rarely",
-        "rather",
-        "really",
-        "seriously",
-        "simply",
-        "so",
-        "somehow",
-        "soon",
-        "sooo*",
-        "still",
-        "such",
-        "there",
-        "theres",
-        "there's",
-        "tho",
-        "though",
-        "too",
-        "totally",
-        "truly",
-        "usually",
-        "very",
-        "well",
-        "when",
-        "whenever",
-        "where",
-        "yet",
-    },
-    "article": {
-        "a",
-        "alot",
-        "an",
-        "the",
-    },
-    "auxvb": {
-        "aint",
-        "ain't",
-        "am",
-        "are",
-        "arent",
-        "aren't",
-        "be",
-        "became",
-        "become",
-        "becomes",
-        "becoming",
-        "been",
-        "being",
-        "can",
-        "cannot",
-        "cant",
-        "can't",
-        "could",
-        "couldnt",
-        "couldn't",
-        "couldve",
-        "could've",
-        "did",
-        "didnt",
-        "didn't",
-        "do",
-        "does",
-        "doesnt",
-        "doesn't",
-        "doing",
-        "done",
-        "dont",
-        "don't",
-        "had",
-        "hadnt",
-        "hadn't",
-        "has",
-        "hasnt",
-        "hasn't",
-        "have",
-        "havent",
-        "haven't",
-        "having",
-        "hed",
-        "he'd",
-        "heres",
-        "here's",
-        "hes",
-        "he's",
-        "Id",
-        "I'd",
-        "I'll",
-        "Im",
[…]

### 2016-10-10 measures/lla.py

@@ -1,20 +1,0 @@
-from . import deps
-
-
-def lla(target, prime):
-    counter = 0
-    for token in target:
-        counter += prime.count(token)
-
-    try:
-        return counter / (len(prime) * len(target))
-    except ZeroDivisionError:
-        return 1.0
-
-
-def lilla(target, prime):
-    return lla(target, prime)
-
-
-def silla(target, prime):
-    return lla(deps.subtrees(target), deps.subtrees(prime))

### 2016-10-10 measures/lsm.py

@@ -1,48 +1,0 @@
-import statistics
-
-from .liwc import LIWC_DATA
-
-
-FUNCTION_CLASSES = {'ADP', 'AUX', 'CONJ', 'DET', 'INTJ', 'NUM', 'PART', 'PRON', 'SCONJ'}
-
-
-def lsm(doc):
-    doc_length = len(doc)
-    function_words = {function_class: 0 for function_class in FUNCTION_CLASSES}
-    for token in doc:
-        if token.pos_ in FUNCTION_CLASSES:
-            function_words[token.pos_] += 1
-
-    return {word_class: (count / doc_length) * 100 for word_class, count in function_words.items()}
-
-
-def liwc_lsm(doc):
-    function_words = {function_class: 0 for function_class in LIWC_DATA}
-    for word in doc:
-        word = word.lower()
-        for function_class in LIWC_DATA:
-            for function_word in function_class:
-                if function_word.endswith('*'):
-                    if word.startswith(function_word[:-1]):
-                        function_words[function_class] += 1
-                else:
-                    if word == function_word:
-                        function_words[function_class] += 1
-
-    return {word_class: (count / len(doc)) * 100 for word_class, count in function_words.items()}
-
-
-def dyad_lsm(doc1, doc2, lsm_func=lsm):
-    lsm1 = lsm_func(doc1)
-    lsm2 = lsm_func(doc2)
-    scores = []
-
-    if lsm_func == liwc_lsm:
-        classes = LIWC_DATA
-    else:
-        classes = FUNCTION_CLASSES
-
-    for word_class in classes:
-        scores.append(1 - abs(lsm1[word_class] - lsm2[word_class]) / (lsm1[word_class] + lsm2[word_class] + .0001))
-
-    return statistics.mean(scores)

### 2016-10-10 parse_ftf.py

@@ -1,173 +1,0 @@
-import os
-import statistics
-
-import matplotlib.pyplot as plt
-from spacy.en import English
-from textblob import TextBlob
-
-from core import constants
-from measures import lla, lsm
-
-
-nlp = English()
-
-
-NEUTRAL_DIR = os.path.join(constants.DATA_DIR, 'ftf', 'Neutral')
-POWER_DIR = os.path.join(constants.DATA_DIR, 'ftf', 'Power')
-
-
-def flatten(conversation):
-    flattened = {}
-    flattened['A'] = '\n'.join(conversation[::2])
-    flattened['B'] = '\n'.join(conversation[1::2])
-    return flattened
-
-
-def parse_flat(flattened):
-    parsed = {'A': {}, 'B': {}}
-    flat_a = flattened['A']
-    flat_b = flattened['B']
-    parsed['A']['spacy'] = nlp(flat_a)
-    parsed['B']['spacy'] = nlp(flat_b)
-    parsed['A']['tb'] = TextBlob(flat_a)
-    parsed['B']['tb'] = TextBlob(flat_b)
-    return parsed
-
-
-def sliding_window(utterances, window_size=1):
-    window_dict = {'A': {}, 'B': {}}
-    for counter, utterance in enumerate(utterances['A']):
-        window_dict['A'][counter] = {'response': utterance, 'cues': []}
-        for window in range(window_size, 0, -1):
-            index = counter - window
-            if index < 0 or index >= len(utterances['B']):
-                continue
-            window_dict['A'][counter]['cues'].append(utterances['B'][index])
-
-    for counter, utterance in enumerate(utterances['B']):
-        window_dict['B'][counter] = {'response': utterance, 'cues': []}
-        for window in range(window_size, 0, -1):
-            index = counter - window + 1
-            if index < 0 or index >= len(utterances['A']):
-                continue
-            window_dict['B'][counter]['cues'].append(utterances['A'][index])
-
-    return window_dict
-
-
-def slider(conversation):
-    utterances = {'A': flatten(conversation)['A'].split('\n'), 'B': flatten(conversation)['B'].split('\n')}
-    windows = {}
-    for window_size in range(1, max(len(utterances['A']), len(utterances['B'])) + 1):
-        windows[window_size] = sliding_window(utterances, window_size)
-
-    return windows
-
-
-def windowed_scores(windows):
-    scores = {}
-    for window_size, conversation in windows.items():
-        scores[window_size] = {}
[…]

### 2016-10-10 run_measures.py

@@ -1,57 +1,0 @@
-import os
-import pickle
-import statistics
-
-from spacy.en import English
-from textblob import TextBlob
-
-from core import constants
-from measures import lla, lsm
-from twtr import utils
-
-
-nlp = English()
-# nlp.vocab.load_vectors(os.path.join(constants.DATA_DIR, 'word2vec_twitter_model.bin'))
-
-
-with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-parsed_chains = utils.parse_chains(chains, escape_html=False)
-
-chain_scores = {}
-for chain_id, chain in parsed_chains.items():
-    messages_a = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[::2]]
-    messages_b = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[1::2]]
-    chain_scores[chain_id] = {}
-
-    lilla_scores = []
-    silla_scores = []
-    lsm_scores = []
-    wv_scores = []
-
-    for counter, message_a in enumerate(messages_a, 1):
-        for message_b in messages_b[counter:]:
-            lilla_scores.append(float(lla.lilla(message_a['textblob'].words, message_b['textblob'].words)))
-            silla_scores.append(float(lla.silla(message_a['spacy'], message_b['spacy'])))
-            lsm_scores.append(float(lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])))
-            wv_scores.append(float(message_a['spacy'].similarity(message_b['spacy'])))
-
-    for counter, message_b in enumerate(messages_b, 1):
-        for message_a in messages_a[counter:]:
-            lilla_scores.append(float(lla.lilla(message_a['textblob'].words, message_b['textblob'].words)))
-            silla_scores.append(float(lla.silla(message_a['spacy'], message_b['spacy'])))
-            lsm_scores.append(float(lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])))
-            wv_scores.append(float(message_a['spacy'].similarity(message_b['spacy'])))
-
-    spacy_a = nlp('\n'.join(chain[::2]))
-    spacy_b = nlp('\n'.join(chain[1::2]))
-
-    chain_scores[chain_id]['lilla'] = statistics.mean(lilla_scores)
[…]

### 2016-10-10 run_scores.py

@@ -1,59 +1,0 @@
-import os
-import pickle
-import statistics
-
-from scipy import stats
-
-from core import constants
-
-
-with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as f:
-    classifications = pickle.load(f)
-
-with open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'rb') as f:
-    scores = pickle.load(f)
-
-lexical_scores = classifications['means']['lexical']
-syntactic_scores = classifications['means']['syntactic']
-semantic_scores = classifications['means']['semantic']
-mean_scores = [statistics.mean(scores) for scores in zip(*[lexical_scores, syntactic_scores, semantic_scores])]
-
-lilla_scores = [score['lilla'] for score in scores.values()]
-silla_scores = [score['silla'] for score in scores.values()]
-wv_scores = [score['wv'] for score in scores.values()]
-wv_conversation_scores = [score['wv_conversation'] for score in scores.values()]
-lsm_scores = [score['lsm'] for score in scores.values()]
-
-
-r, p = stats.pearsonr(lexical_scores, lilla_scores)
-print('Lexical vs LILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
-
-r, p = stats.pearsonr(syntactic_scores, silla_scores)
-print('Syntactic vs SILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
-
-r, p = stats.pearsonr(semantic_scores, wv_scores)
-print('Semantic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
-
-r, p = stats.pearsonr(lexical_scores, wv_scores)
-print('Lexical vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
-
-r, p = stats.pearsonr(syntactic_scores, wv_scores)
-print('Syntactic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
-
-r, p = stats.pearsonr(mean_scores, wv_scores)
-print('Mean vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
-
-r, p = stats.pearsonr(semantic_scores, wv_conversation_scores)
-print('Semantic vs Word2vec (conversation): r={r}, p={p:.20f}'.format(r=r, p=p))
-
[…]

### 2016-10-10 save_classifications.py

@@ -1,40 +1,0 @@
-import argparse
-import csv
-import os
-import pickle
-import statistics
-
-from core import constants
-
-
-def get_means(classifications, category):
-    scores_zip = zip(*[classifier[category] for classifier in classifications['classifiers'].values()])
-    return [statistics.mean(scores) for scores in scores_zip]
-
-
-parser = argparse.ArgumentParser()
-parser.add_argument('infiles', nargs='+', type=argparse.FileType('r'))
-args = parser.parse_args()
-
-classifications = {
-    'classifiers': {},
-    'means': {},
-}
-for classifier, csvfile in enumerate(args.infiles, 1):
-    classifications['classifiers'][classifier] = {
-        'lexical': [],
-        'syntactic': [],
-        'semantic': [],
-    }
-    reader = csv.DictReader(csvfile)
-    for row in reader:
-        classifications['classifiers'][classifier]['lexical'].append(int(row['Lexical']))
-        classifications['classifiers'][classifier]['syntactic'].append(int(row['Syntactic']))
-        classifications['classifiers'][classifier]['semantic'].append(int(row['Semantic']))
-
-classifications['means']['lexical'] = get_means(classifications, 'lexical')
-classifications['means']['syntactic'] = get_means(classifications, 'syntactic')
-classifications['means']['semantic'] = get_means(classifications, 'semantic')
-
-with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'wb') as f:
-    pickle.dump(classifications, f)

### 2016-10-10 twtr/get_tweets.py

@@ -1,88 +1,0 @@
-import os
-import pickle
-import sys
-
-import tweepy
-
-from core import constants
-
-
-CONSUMER_KEY = os.environ['TWITTER_CONSUMER_KEY']
-CONSUMER_SECRET = os.environ['TWITTER_CONSUMER_SECRET']
-ACCESS_TOKEN = os.environ['TWITTER_ACCESS_TOKEN']
-ACCESS_TOKEN_SECRET = os.environ['ACCESS_TOKEN_SECRET']
-
-
-auth = tweepy.OAuthHandler(CONSUMER_KEY, CONSUMER_SECRET)
-auth.set_access_token(ACCESS_TOKEN, ACCESS_TOKEN_SECRET)
-
-api = tweepy.API(auth, wait_on_rate_limit=True, wait_on_rate_limit_notify=True)
-
-
-def get_status_chain(api, status_id):
-    """Given a status ID, iterate up the chain of tweets and return them in order.
-
-    This function doesn't look further down the chain, it only looks up, so it could be incomplete.
-    We also stop short if we hit a third author, as we only care about dyads.
-
-    Keyword arguments:
-    api -- tweepy API object
-    status_id -- ID of the status to start from
-    """
-    authors = []
-    statuses = []
-
-    while True:
-        status = api.get_status(status_id)
-        author = status.author.screen_name
-
-        # Check we're in a dyadic conversation.
-        if len(authors) < 2 and author not in authors:
-            authors.append(author)
-        elif author not in authors:
-            # No longer a dyad, cut off at this status and only use the dyadic part.
-            break
-
-        statuses.append(status)
-
-        if not status.in_reply_to_status_id_str:
-            break
-
-        status_id = status.in_reply_to_status_id_str
-
-    statuses.reverse()
-    return statuses
-
-
-chains = []
-
-page = 1
-while len(chains) < 200:
-    statuses = None
-    while statuses is None:
-        try:
-            statuses = api.search(q='filter:replies', count=100, lang='en')
-        except Exception as e:
-            print('Error: {error}. Retrying.'.format(error=e), file=sys.stderr)
-
-    if statuses:
-        for status in statuses:
-            try:
-                status_chain = get_status_chain(api, status.id_str)
-                if len(status_chain) > 9:
-                    chains.append(status_chain)
-            except Exception as e:
-                # We hit a private message or a connection issue, skip to the next.
[…]

### 2016-10-10 twtr/select_tweets.py

@@ -1,31 +1,0 @@
-import os
-import pickle
-
-from distutils.util import strtobool
-
-from core import constants
-
-
-def query_yes_no(question, default="yes"):
-    print('{question} [y/n]'.format(question=question))
-    while True:
-        try:
-            return strtobool(input().lower())
-        except ValueError:
-            print("Please respond with 'y' or 'n'.")
-
-
-with open(os.path.join(constants.DATA_DIR, 'tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-keepers = []
-for chain in chains:
-    for status in chain:
-        print('{author}: {status}'.format(author=status.author.screen_name, status=status.text))
-    is_keeper = query_yes_no('Do you want to keep this chain?')
-
-    if is_keeper:
-        keepers.append(chain)
-
-with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'wb') as f:
-    pickle.dump(keepers, f)

### 2016-10-10 twtr/tweets_to_text.py

@@ -1,16 +1,0 @@
-import os
-import pickle
-
-from core import constants
-
-
-with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
-    chains = pickle.load(f)
-
-
-with open('data.txt', 'w') as f:
-    for counter, chain in enumerate(chains, 1):
-        f.write('Chain {num}\n'.format(num=counter))
-        for status in chain:
-            f.write('{author}: {status}\n'.format(author=status.author.screen_name, status=status.text))
-        f.write('------------------------------------------------\n\n')

### 2016-10-10 twtr/utils.py

@@ -1,55 +1,0 @@
-import html
-import itertools
-import validators
-
-
-def normalise_urls(text):
-    for word in text.split(' '):
-        if validators.url(word):
-            text = text.replace(word, '[URL]')
-    return text
-
-
-def normalise_screen_names(text):
-    for word in text.split(' '):
-        if word.startswith('@'):
-            text = text.replace(word, '[MENTION]')
-    return text
-
-
-def remove_screen_names(text):
-    while True:
-        text = text.lstrip()
-        word = text.split(' ')[0]
-        if not word.startswith('@'):
-            break
-
-        text = text.replace(word, '')
-    return text
-
-
-def format_message(text, escape_html=True, is_ham=False):
-    if is_ham:
-        text = normalise_screen_names(text)
-    else:
-        text = remove_screen_names(text)
-    text = normalise_urls(text)
-    if escape_html:
-        text = html.unescape(text)
-    return text.strip()
-
-
-def parse_chains(chains, escape_html=True):
-    parsed_chains = {}
-    for counter, chain in enumerate(chains):
-        messages = []
-        for key, group in itertools.groupby(chain, lambda x: x.author.screen_name):
-            merged = []
-            for status in group:
-                merged.append(format_message(status.text, escape_html))
-
-            merged = '\n'.join(merged)
-            messages.append(merged)
-
-        parsed_chains[counter] = messages
-    return parsed_chains

### 2016-10-10 la/classifier_correlation.py
Rejiggy

@@ -1,0 +1,31 @@
+import itertools
+import os
+import pickle
+
+from scipy import stats
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as f:
+    classifications = pickle.load(f)
+
+pairs = itertools.combinations(classifications['classifiers'].keys(), 2)
+
+for classifier_a, classifier_b in pairs:
+    print('Classifiers', classifier_a, 'and', classifier_b)
+
+    lexical_a = classifications['classifiers'][classifier_a]['lexical']
+    lexical_b = classifications['classifiers'][classifier_b]['lexical']
+    r, p = stats.pearsonr(lexical_a, lexical_b)
+    print('Lexical: r={r}, p={p}'.format(r=r, p=p))
+
+    syntactic_a = classifications['classifiers'][classifier_a]['syntactic']
+    syntactic_b = classifications['classifiers'][classifier_b]['syntactic']
+    r, p = stats.pearsonr(syntactic_a, syntactic_b)
+    print('Syntactic: r={r}, p={p}'.format(r=r, p=p))
+
+    semantic_a = classifications['classifiers'][classifier_a]['semantic']
+    semantic_b = classifications['classifiers'][classifier_b]['semantic']
+    r, p = stats.pearsonr(semantic_a, semantic_b)
+    print('Semantic: r={r}, p={p}'.format(r=r, p=p))

### 2016-10-10 la/core/constants.py

@@ -1,0 +1,6 @@
+import os
+
+
+BASE_DIR = BASE_DIR = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))
+DATA_DIR = os.path.join(BASE_DIR, 'data')
+HTML_DIR = os.path.join(BASE_DIR, 'html')

### 2016-10-10 la/ftf_predict.py

@@ -1,0 +1,39 @@
+import os
+import pickle
+import statistics
+
+from sklearn.cross_validation import cross_val_score
+from sklearn.linear_model import LinearRegression
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import PolynomialFeatures
+from sklearn import svm
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_neutral_window.pickle'), 'rb') as f:
+    neutral_window_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_power_window.pickle'), 'rb') as f:
+    power_window_scores = pickle.load(f)
+
+window_sizes = []
+mean_scores = []
+
+for conversation in power_window_scores + neutral_window_scores:
+    means = []
+    max_window_size = 0
+    for window_size, parsed in conversation.items():
+        means.append(parsed['mean']['lsm'])
+        max_window_size = max(max_window_size, window_size)
+    mean_scores.append([statistics.mean(means)])
+    window_sizes.append(max_window_size)
+
+clf = svm.SVC(kernel='linear', C=1)
+model = Pipeline([('poly', PolynomialFeatures(degree=3)), ('linear', LinearRegression())])
+
+scores = cross_val_score(clf, mean_scores, window_sizes, cv=5)
+print('SVC Accuracy: {} (+/- {})'.format(scores.mean(), scores.std() * 2))
+
+scores = cross_val_score(model, mean_scores, window_sizes, cv=5)
+print('PR Accuracy: {} (+/- {})'.format(scores.mean(), scores.std() * 2))

### 2016-10-10 la/ftf_results.py

@@ -1,0 +1,298 @@
+import collections
+import os
+import pickle
+import statistics
+
+import numpy as np
+from matplotlib import pyplot as plt
+from scipy import stats
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_neutral_flat.pickle'), 'rb') as f:
+    neutral_flat_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_power_flat.pickle'), 'rb') as f:
+    power_flat_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_neutral_window.pickle'), 'rb') as f:
+    neutral_window_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_power_window.pickle'), 'rb') as f:
+    power_window_scores = pickle.load(f)
+
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_short_neutral_flat.pickle'), 'rb') as f:
+    short_neutral_flat_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_short_power_flat.pickle'), 'rb') as f:
+    short_power_flat_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_short_neutral_window.pickle'), 'rb') as f:
+    short_neutral_window_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_short_power_window.pickle'), 'rb') as f:
+    short_power_window_scores = pickle.load(f)
+
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_very_short_neutral_window.pickle'), 'rb') as f:
+    very_short_neutral_window_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_very_short_power_window.pickle'), 'rb') as f:
+    very_short_power_window_scores = pickle.load(f)
+
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_random_very_short_neutral_window.pickle'), 'rb') as f:
+    random_very_short_neutral_window_scores = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'ftf_random_very_short_power_window.pickle'), 'rb') as f:
+    random_very_short_power_window_scores = pickle.load(f)
+
+
+'''LSM'''
+
[…]

### 2016-10-10 la/generate_csv.py

@@ -1,0 +1,11 @@
+import csv
+import os
+
+from core import constants
+
+
+with open(os.path.join(constants.HTML_DIR, 'classifications.csv'), 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(['', 'Lexical', 'Syntactic', 'Semantic'])
+    for row in range(103):
+        writer.writerow(['Conversation {counter}'.format(counter=row + 1), '', '', ''])

### 2016-10-10 la/generate_data_csv.py

@@ -1,0 +1,25 @@
+import csv
+import itertools
+import os
+import pickle
+
+from core import constants
+from twtr import utils
+
+
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+parsed_chains = utils.parse_chains(chains)
+
+with open(os.path.join(constants.DATA_DIR, 'data.csv'), 'w') as csvfile:
+    writer = csv.writer(csvfile)
+    writer.writerow(['Text'])
+    for chain in parsed_chains.values():
+        row = ''
+        author = itertools.cycle('AB')
+        for message in chain:
+            row += '<p><strong>{author}</strong>: {message}</p>'.format(
+                author=next(author), message=message
+            ).replace('\n', '<br>')
+        writer.writerow([row])

### 2016-10-10 la/generate_html.py

@@ -1,0 +1,41 @@
+import itertools
+import os
+import pickle
+
+from core import constants
+from twtr import utils
+
+
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+parsed_chains = utils.parse_chains(chains)
+
+html = """
+<meta charset="utf-8">
+<title>Messages to classify</title>
+<style>
+  @font-face {
+    font-family: 'Symbola';
+    src: url('Symbola.ttf') format('truetype');
+    text-decoration: none;
+    font-style: normal;
+  }
+  body {
+    font-family: 'Symbola', sans-serif;
+    line-height: 1;
+    font-size: 24px;
+  }
+</style>
+"""
+
+for counter, chain in parsed_chains.items():
+    html += '<h1>Conversation {counter}</h1>'.format(counter=counter + 1)
+    author = itertools.cycle('AB')
+    for message in chain:
+        html += '<p><strong>{author}</strong>: {message}</p>'.format(
+            author=next(author), message=message
+        ).replace('\n', '<br>')
+
+with open(os.path.join(constants.HTML_DIR, 'messages.html'), 'w') as f:
+    f.write(html)

### 2016-10-10 la/iam_correlations.py

@@ -1,0 +1,30 @@
+import itertools
+import os
+import pickle
+
+from scipy import stats
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as c, \
+        open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'rb') as s:
+    classifications = pickle.load(c)
+    scores = pickle.load(s)
+
+
+scores_dict = {}
+for measure in ['lsm', 'lilla', 'silla', 'wv']:
+    scores_dict[measure] = [chain_scores[measure] for chain_scores in scores.values()]
+
+for measure_a, measure_b in itertools.combinations(scores_dict.keys(), 2):
+    print(measure_a, 'vs', measure_b)
+    r, p = stats.pearsonr(scores_dict[measure_a], scores_dict[measure_b])
+    print('r={r}, p={p:.20f}'.format(r=r, p=p))
+
+print()
+
+for category_a, category_b in itertools.combinations(classifications['means'].keys(), 2):
+    print(category_a, 'vs', category_b)
+    r, p = stats.pearsonr(classifications['means'][category_a], classifications['means'][category_b])
+    print('r={r}, p={p:.20f}'.format(r=r, p=p))

### 2016-10-10 la/measures/liwc.py

@@ -1,0 +1,587 @@
+LIWC_DATA = {
+    "adverbs": {
+        "about",
+        "absolutely",
+        "actually",
+        "again",
+        "also",
+        "anyway*",
+        "anywhere",
+        "apparently",
+        "around",
+        "back",
+        "basically",
+        "beyond",
+        "clearly",
+        "completely",
+        "constantly",
+        "definitely",
+        "especially",
+        "even",
+        "eventually",
+        "ever",
+        "frequently",
+        "generally",
+        "here",
+        "heres",
+        "here's",
+        "hopefully",
+        "how",
+        "however",
+        "immediately",
+        "instead",
+        "just",
+        "lately",
+        "maybe",
+        "mostly",
+        "nearly",
+        "now",
+        "often",
+        "only",
+        "perhaps",
+        "primarily",
+        "probably",
+        "push*",
+        "quick*",
+        "rarely",
+        "rather",
+        "really",
+        "seriously",
+        "simply",
+        "so",
+        "somehow",
+        "soon",
+        "sooo*",
+        "still",
+        "such",
+        "there",
+        "theres",
+        "there's",
+        "tho",
+        "though",
+        "too",
+        "totally",
+        "truly",
+        "usually",
+        "very",
+        "well",
+        "when",
+        "whenever",
+        "where",
+        "yet",
+    },
+    "article": {
+        "a",
+        "alot",
+        "an",
+        "the",
+    },
+    "auxvb": {
+        "aint",
+        "ain't",
+        "am",
+        "are",
+        "arent",
+        "aren't",
+        "be",
+        "became",
+        "become",
+        "becomes",
+        "becoming",
+        "been",
+        "being",
+        "can",
+        "cannot",
+        "cant",
+        "can't",
+        "could",
+        "couldnt",
+        "couldn't",
+        "couldve",
+        "could've",
+        "did",
+        "didnt",
+        "didn't",
+        "do",
+        "does",
+        "doesnt",
+        "doesn't",
+        "doing",
+        "done",
+        "dont",
+        "don't",
+        "had",
+        "hadnt",
+        "hadn't",
+        "has",
+        "hasnt",
+        "hasn't",
+        "have",
+        "havent",
+        "haven't",
+        "having",
+        "hed",
+        "he'd",
+        "heres",
+        "here's",
+        "hes",
+        "he's",
+        "Id",
+        "I'd",
+        "I'll",
+        "Im",
[…]

### 2016-10-10 la/measures/lla.py

@@ -1,0 +1,20 @@
+from . import deps
+
+
+def lla(target, prime):
+    counter = 0
+    for token in target:
+        counter += prime.count(token)
+
+    try:
+        return counter / (len(prime) * len(target))
+    except ZeroDivisionError:
+        return 1.0
+
+
+def lilla(target, prime):
+    return lla(target, prime)
+
+
+def silla(target, prime):
+    return lla(deps.subtrees(target), deps.subtrees(prime))

### 2016-10-10 la/measures/lsm.py

@@ -1,0 +1,47 @@
+import statistics
+
+from .liwc import LIWC_DATA
+
+
+FUNCTION_CLASSES = {'ADP', 'AUX', 'CONJ', 'DET', 'INTJ', 'NUM', 'PART', 'PRON', 'SCONJ'}
+
+
+def lsm(doc):
+    function_words = {function_class: 0 for function_class in FUNCTION_CLASSES}
+    for token in doc:
+        if token.pos_ in FUNCTION_CLASSES:
+            function_words[token.pos_] += 1
+
+    return {word_class: (count / len(doc)) * 100 for word_class, count in function_words.items()}
+
+
+def liwc_lsm(doc):
+    function_words = {function_class: 0 for function_class in LIWC_DATA}
+    for word in doc:
+        word = word.lower()
+        for function_class in LIWC_DATA:
+            for function_word in function_class:
+                if function_word.endswith('*'):
+                    if word.startswith(function_word[:-1]):
+                        function_words[function_class] += 1
+                else:
+                    if word == function_word:
+                        function_words[function_class] += 1
+
+    return {word_class: (count / (len(doc) or 0.00001)) * 100 for word_class, count in function_words.items()}
+
+
+def dyad_lsm(doc1, doc2, lsm_func=lsm):
+    lsm1 = lsm_func(doc1)
+    lsm2 = lsm_func(doc2)
+    scores = []
+
+    if lsm_func == liwc_lsm:
+        classes = LIWC_DATA
+    else:
+        classes = FUNCTION_CLASSES
+
+    for word_class in classes:
+        scores.append(1 - abs(lsm1[word_class] - lsm2[word_class]) / (lsm1[word_class] + lsm2[word_class] + .0001))
+
+    return statistics.mean(scores)

### 2016-10-10 la/parse_ftf.py

@@ -1,0 +1,294 @@
+import os
+import pickle
+import random
+import statistics
+
+from textblob import TextBlob
+
+from core import constants
+from measures import lla, lsm
+
+
+NEUTRAL_DIR = os.path.join(constants.DATA_DIR, 'ftf', 'Neutral')
+POWER_DIR = os.path.join(constants.DATA_DIR, 'ftf', 'Power')
+
+
+def flatten(conversation):
+    flattened = {}
+    flattened['A'] = '\n'.join(conversation[::2])
+    flattened['B'] = '\n'.join(conversation[1::2])
+    return flattened
+
+
+def parse_flat(flattened):
+    parsed = {'A': {}, 'B': {}}
+    flat_a = flattened['A']
+    flat_b = flattened['B']
+    parsed['A']['tb'] = TextBlob(flat_a)
+    parsed['B']['tb'] = TextBlob(flat_b)
+    return parsed
+
+
+def flat_scores(conversation):
+    conversation = parse_flat(flatten(conversation))
+    score = {
+        'lsm': lsm.dyad_lsm(conversation['A']['tb'].words, conversation['B']['tb'].words, lsm_func=lsm.liwc_lsm),
+        'lilla': lla.lilla(conversation['A']['tb'].words, conversation['B']['tb'].words),
+    }
+    return score
+
+
+def sliding_window(utterances, window_size=1):
+    window_dict = {'A': {}, 'B': {}}
+    for counter, utterance in enumerate(utterances['A']):
+        window_dict['A'][counter] = {'response': utterance, 'cues': []}
+        for window in range(window_size, 0, -1):
+            index = counter - window
+            if index < 0 or index >= len(utterances['B']):
+                continue
+            window_dict['A'][counter]['cues'].append(utterances['B'][index])
+
+    for counter, utterance in enumerate(utterances['B']):
+        window_dict['B'][counter] = {'response': utterance, 'cues': []}
+        for window in range(window_size, 0, -1):
+            index = counter - window + 1
+            if index < 0 or index >= len(utterances['A']):
+                continue
+            window_dict['B'][counter]['cues'].append(utterances['A'][index])
+
+    return window_dict
+
+
+def slider(conversation):
+    utterances = {'A': flatten(conversation)['A'].split('\n'), 'B': flatten(conversation)['B'].split('\n')}
+    windows = {}
+    for window_size in range(1, max(len(utterances['A']), len(utterances['B'])) + 1):
[…]

### 2016-10-10 la/run_measures.py

@@ -1,0 +1,57 @@
+import os
+import pickle
+import statistics
+
+from spacy.en import English
+from textblob import TextBlob
+
+from core import constants
+from measures import lla, lsm
+from twtr import utils
+
+
+nlp = English()
+# nlp.vocab.load_vectors(os.path.join(constants.DATA_DIR, 'word2vec_twitter_model.bin'))
+
+
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+parsed_chains = utils.parse_chains(chains, escape_html=False)
+
+chain_scores = {}
+for chain_id, chain in parsed_chains.items():
+    messages_a = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[::2]]
+    messages_b = [{'textblob': TextBlob(message), 'spacy': nlp(message)} for message in chain[1::2]]
+    chain_scores[chain_id] = {}
+
+    lilla_scores = []
+    silla_scores = []
+    lsm_scores = []
+    wv_scores = []
+
+    for counter, message_a in enumerate(messages_a, 1):
+        for message_b in messages_b[counter:]:
+            lilla_scores.append(float(lla.lilla(message_a['textblob'].words, message_b['textblob'].words)))
+            silla_scores.append(float(lla.silla(message_a['spacy'], message_b['spacy'])))
+            lsm_scores.append(float(lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])))
+            wv_scores.append(float(message_a['spacy'].similarity(message_b['spacy'])))
+
+    for counter, message_b in enumerate(messages_b, 1):
+        for message_a in messages_a[counter:]:
+            lilla_scores.append(float(lla.lilla(message_a['textblob'].words, message_b['textblob'].words)))
+            silla_scores.append(float(lla.silla(message_a['spacy'], message_b['spacy'])))
+            lsm_scores.append(float(lsm.dyad_lsm(message_a['spacy'], message_b['spacy'])))
+            wv_scores.append(float(message_a['spacy'].similarity(message_b['spacy'])))
+
+    spacy_a = nlp('\n'.join(chain[::2]))
+    spacy_b = nlp('\n'.join(chain[1::2]))
+
+    chain_scores[chain_id]['lilla'] = statistics.mean(lilla_scores)
[…]

### 2016-10-10 la/run_scores.py

@@ -1,0 +1,59 @@
+import os
+import pickle
+import statistics
+
+from scipy import stats
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'classifications.pickle'), 'rb') as f:
+    classifications = pickle.load(f)
+
+with open(os.path.join(constants.DATA_DIR, 'scores.pickle'), 'rb') as f:
+    scores = pickle.load(f)
+
+lexical_scores = classifications['means']['lexical']
+syntactic_scores = classifications['means']['syntactic']
+semantic_scores = classifications['means']['semantic']
+mean_scores = [statistics.mean(scores) for scores in zip(*[lexical_scores, syntactic_scores, semantic_scores])]
+
+lilla_scores = [score['lilla'] for score in scores.values()]
+silla_scores = [score['silla'] for score in scores.values()]
+wv_scores = [score['wv'] for score in scores.values()]
+wv_conversation_scores = [score['wv_conversation'] for score in scores.values()]
+lsm_scores = [score['lsm'] for score in scores.values()]
+
+
+r, p = stats.pearsonr(lexical_scores, lilla_scores)
+print('Lexical vs LILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(syntactic_scores, silla_scores)
+print('Syntactic vs SILLA: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(semantic_scores, wv_scores)
+print('Semantic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(lexical_scores, wv_scores)
+print('Lexical vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(syntactic_scores, wv_scores)
+print('Syntactic vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(mean_scores, wv_scores)
+print('Mean vs Word2vec: r={r}, p={p:.20f}'.format(r=r, p=p))
+
+r, p = stats.pearsonr(semantic_scores, wv_conversation_scores)
+print('Semantic vs Word2vec (conversation): r={r}, p={p:.20f}'.format(r=r, p=p))
+
[…]

### 2016-10-10 la/twtr/get_tweets.py

@@ -1,0 +1,88 @@
+import os
+import pickle
+import sys
+
+import tweepy
+
+from core import constants
+
+
+CONSUMER_KEY = os.environ['TWITTER_CONSUMER_KEY']
+CONSUMER_SECRET = os.environ['TWITTER_CONSUMER_SECRET']
+ACCESS_TOKEN = os.environ['TWITTER_ACCESS_TOKEN']
+ACCESS_TOKEN_SECRET = os.environ['ACCESS_TOKEN_SECRET']
+
+
+auth = tweepy.OAuthHandler(CONSUMER_KEY, CONSUMER_SECRET)
+auth.set_access_token(ACCESS_TOKEN, ACCESS_TOKEN_SECRET)
+
+api = tweepy.API(auth, wait_on_rate_limit=True, wait_on_rate_limit_notify=True)
+
+
+def get_status_chain(api, status_id):
+    """Given a status ID, iterate up the chain of tweets and return them in order.
+
+    This function doesn't look further down the chain, it only looks up, so it could be incomplete.
+    We also stop short if we hit a third author, as we only care about dyads.
+
+    Keyword arguments:
+    api -- tweepy API object
+    status_id -- ID of the status to start from
+    """
+    authors = []
+    statuses = []
+
+    while True:
+        status = api.get_status(status_id)
+        author = status.author.screen_name
+
+        # Check we're in a dyadic conversation.
+        if len(authors) < 2 and author not in authors:
+            authors.append(author)
+        elif author not in authors:
+            # No longer a dyad, cut off at this status and only use the dyadic part.
+            break
+
+        statuses.append(status)
+
+        if not status.in_reply_to_status_id_str:
+            break
+
+        status_id = status.in_reply_to_status_id_str
+
+    statuses.reverse()
+    return statuses
+
+
+chains = []
+
+page = 1
+while len(chains) < 200:
+    statuses = None
+    while statuses is None:
+        try:
+            statuses = api.search(q='filter:replies', count=100, lang='en')
+        except Exception as e:
+            print('Error: {error}. Retrying.'.format(error=e), file=sys.stderr)
+
+    if statuses:
+        for status in statuses:
+            try:
+                status_chain = get_status_chain(api, status.id_str)
+                if len(status_chain) > 9:
+                    chains.append(status_chain)
+            except Exception as e:
+                # We hit a private message or a connection issue, skip to the next.
[…]

### 2016-10-10 la/twtr/select_tweets.py

@@ -1,0 +1,31 @@
+import os
+import pickle
+
+from distutils.util import strtobool
+
+from core import constants
+
+
+def query_yes_no(question, default="yes"):
+    print('{question} [y/n]'.format(question=question))
+    while True:
+        try:
+            return strtobool(input().lower())
+        except ValueError:
+            print("Please respond with 'y' or 'n'.")
+
+
+with open(os.path.join(constants.DATA_DIR, 'tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+keepers = []
+for chain in chains:
+    for status in chain:
+        print('{author}: {status}'.format(author=status.author.screen_name, status=status.text))
+    is_keeper = query_yes_no('Do you want to keep this chain?')
+
+    if is_keeper:
+        keepers.append(chain)
+
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'wb') as f:
+    pickle.dump(keepers, f)

### 2016-10-10 la/twtr/tweets_to_text.py

@@ -1,0 +1,16 @@
+import os
+import pickle
+
+from core import constants
+
+
+with open(os.path.join(constants.DATA_DIR, 'selected_tweets.pickle'), 'rb') as f:
+    chains = pickle.load(f)
+
+
+with open('data.txt', 'w') as f:
+    for counter, chain in enumerate(chains, 1):
+        f.write('Chain {num}\n'.format(num=counter))
+        for status in chain:
+            f.write('{author}: {status}\n'.format(author=status.author.screen_name, status=status.text))
+        f.write('------------------------------------------------\n\n')

### 2016-10-10 la/twtr/utils.py

@@ -1,0 +1,55 @@
+import html
+import itertools
+import validators
+
+
+def normalise_urls(text):
+    for word in text.split(' '):
+        if validators.url(word):
+            text = text.replace(word, '[URL]')
+    return text
+
+
+def normalise_screen_names(text):
+    for word in text.split(' '):
+        if word.startswith('@'):
+            text = text.replace(word, '[MENTION]')
+    return text
+
+
+def remove_screen_names(text):
+    while True:
+        text = text.lstrip()
+        word = text.split(' ')[0]
+        if not word.startswith('@'):
+            break
+
+        text = text.replace(word, '')
+    return text
+
+
+def format_message(text, escape_html=True, is_ham=False):
+    if is_ham:
+        text = normalise_screen_names(text)
+    else:
+        text = remove_screen_names(text)
+    text = normalise_urls(text)
+    if escape_html:
+        text = html.unescape(text)
+    return text.strip()
+
+
+def parse_chains(chains, escape_html=True):
+    parsed_chains = {}
+    for counter, chain in enumerate(chains):
+        messages = []
+        for key, group in itertools.groupby(chain, lambda x: x.author.screen_name):
+            merged = []
+            for status in group:
+                merged.append(format_message(status.text, escape_html))
+
+            merged = '\n'.join(merged)
+            messages.append(merged)
+
+        parsed_chains[counter] = messages
+    return parsed_chains
